---
title: "Descriptive analysis of coefficient of variation"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Roboto+Condensed:wght@400;700&display=swap');

table {
  font-family: 'Roboto Condensed', sans-serif;
}
```

This article shows how to calculate the descriptive analysis of coefficient of 
variation for emission profile, sector profile, and transition risk profile.

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
library(tiltDataAnalysis)
library(dplyr)
library(kableExtra)
library(knitr)
library(stringr)
options(readr.show_col_types = FALSE)
```

### Example company-level output of transition risk profile for `cov_emission_rank`

```{r, echo= FALSE}
# read_csv("transition_risk_profile_at_company_level_29_01_25.csv")
emission_company_example <- example_transition_risk_product_emission_cov()
kable(emission_company_example |> head(20))
```

### Average `cov_emission_rank` per company for emission profile benchmarks

```{r}
avg_cov_emission_rank_per_benchmark <- emission_company_example |>
  select(all_of(c("companies_id", "grouping_emission", "cov_emission_rank"))) |>
  filter(!is.na(cov_emission_rank)) |>
  distinct() |>
  mutate(sum_cov_emission_rank = sum(.data$cov_emission_rank, na.rm = TRUE), .by = "grouping_emission") |>
  mutate(distinct_companies_per_benchmark = n_distinct(.data$companies_id, na.rm = TRUE), .by = "grouping_emission") |>
  mutate("Average COV of emission rank for all firms" = sum_cov_emission_rank/distinct_companies_per_benchmark) |>
  select(-all_of(c("sum_cov_emission_rank", "distinct_companies_per_benchmark", "cov_emission_rank", "companies_id"))) |>
  distinct() |>
  filter(grouping_emission %in% c("unit", "unit_tilt_subsector", "unit_isic_4digit")) |>
  rename("group" = "grouping_emission")
```

```{r, echo=FALSE}
kable(avg_cov_emission_rank_per_benchmark, align = "lc", caption = "Average COV of emission rank for all firms per group", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(2, width = "5cm")
```

### Example company-level output of transition risk profile for `cov_sector_target`

```{r, echo= FALSE}
# read_csv("transition_risk_profile_at_company_level_23_10_24.csv")
sector_company_example <- example_transition_risk_product_sector_cov()
kable(sector_company_example |> head(20))
```

### Average `cov_sector_target` per company for grouping_sector

```{r, echo=FALSE}
avg_cov_sector_target_per_benchmark <- sector_company_example |>
  select(all_of(c("companies_id", "scenario", "year", "cov_sector_target"))) |>
  mutate(grouping_sector = paste(.data$scenario, .data$year, sep = "_")) |>
  select(-all_of(c("scenario", "year"))) |>
  distinct() |>
  filter(!is.na(cov_sector_target)) |>
  mutate(sum_cov_sector_target = sum(.data$cov_sector_target, na.rm = TRUE), .by = "grouping_sector") |>
  mutate(distinct_companies_per_benchmark = n_distinct(.data$companies_id, na.rm = TRUE), .by = "grouping_sector") |>
  mutate("Average COV of sector target for all firms" = sum_cov_sector_target/distinct_companies_per_benchmark) |>
  select(-all_of(c("sum_cov_sector_target", "distinct_companies_per_benchmark", "cov_sector_target", "companies_id"))) |>
  distinct() |>
  filter(!str_detect(grouping_sector, "NA")) |>
  rename("scenario" = "grouping_sector")
```

```{r, echo=FALSE}
kable(avg_cov_sector_target_per_benchmark, align = "lc", caption = "Average COV of sector target for all firms per scenario", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(2, width = "5cm")
```

### Example company-level output of transition risk profile for `cov_transition_risk`

```{r, echo= FALSE}
# read_csv("transition_risk_profile_at_company_level_29_01_25.csv")
transition_risk_company_example <- example_transition_risk_product_transition_risk_cov()
kable(transition_risk_company_example |> head(20))
```

### Average `cov_transition_risk` per company for tilt_subsector benchmarks of grouping_transition_risk

```{r, echo=FALSE}
avg_cov_transition_risk_per_benchmark <- transition_risk_company_example |>
  select(all_of(c("companies_id", "grouping_transition_risk", "cov_transition_risk"))) |>
  distinct() |>
  filter(grouping_transition_risk %in% c("1.5C RPS_2030_unit", "1.5C RPS_2050_unit",
                                         "NZ 2050_2030_unit", "NZ 2050_2050_unit",
                                         "1.5C RPS_2030_unit_tilt_subsector", "1.5C RPS_2050_unit_tilt_subsector",
                                         "NZ 2050_2030_unit_tilt_subsector", "NZ 2050_2050_unit_tilt_subsector",
                                         "1.5C RPS_2030_unit_isic_4digit", "1.5C RPS_2050_unit_isic_4digit",
                                         "NZ 2050_2030_unit_isic_4digit", "NZ 2050_2050_unit_isic_4digit")) |>
  filter(!is.na(cov_transition_risk)) |>
  mutate(sum_cov_transition_risk = sum(.data$cov_transition_risk, na.rm = TRUE), .by = "grouping_transition_risk") |>
  mutate(distinct_companies_per_benchmark = n_distinct(.data$companies_id, na.rm = TRUE), .by = "grouping_transition_risk") |>
  mutate("Average COV of transition risk for all firms" = sum_cov_transition_risk/distinct_companies_per_benchmark) |>
  select(-all_of(c("sum_cov_transition_risk", "distinct_companies_per_benchmark", "cov_transition_risk", "companies_id"))) |>
  distinct()

avg_cov_transition_risk_per_benchmark$group <- sub(".*?_((tilt|unit|all).*)", "\\1", avg_cov_transition_risk_per_benchmark$grouping_transition_risk)
avg_cov_transition_risk_per_benchmark$scenario <- sub("_((?:tilt|unit|all).*)", "", avg_cov_transition_risk_per_benchmark$grouping_transition_risk)
avg_cov_transition_risk_per_benchmark <- avg_cov_transition_risk_per_benchmark |>
  select(-all_of(c("grouping_transition_risk"))) |>
  relocate(all_of(c("group", "scenario")))

```

```{r, echo=FALSE}
kable(avg_cov_transition_risk_per_benchmark, align = "llc", caption = "Average COV of transition risk for all firms per scenario of `tilt_subsector` group", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3, width = "5cm") |>
  collapse_rows(columns = 1, valign = "top")
```

