---
title: "Descriptive analysis of products"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Roboto+Condensed:wght@400;700&display=swap');

table {
  font-family: 'Roboto Condensed', sans-serif;
}
```

This article shows how to calculate the descriptive analysis of products for 
emission and sector profile.

```{r setup, warning=FALSE, echo = FALSE, message=FALSE}
library(kableExtra)
library(dplyr)
library(knitr)
library(tiltDataAnalysis)
library(stringr)
library(tiltToyData)
library(readr)
options(readr.show_col_types = FALSE)
```

### Distinct europages products

#### Input

```{r, echo=FALSE}
example_europages_companies <- read_csv(toy_europages_companies()) |> head(10)
kable(example_europages_companies)
```

#### Output

```{r, results='asis'}
cat("Distinct europages products:", n_distinct(example_europages_companies$clustered))
```

### Distinct europages products that matched to ecoinvent

#### Input

```{r, echo=FALSE}
# base_input <- read_csv("transition_risk_profile_at_product_level_all_countries_wide_22_08_24.csv")
example_emission_profile <- example_transition_risk_emission_ep_product_des_analysis()
kable(example_emission_profile)
```

#### Output

```{r, echo=FALSE}
matched_ecoinvent <- example_emission_profile |>
  select(all_of(c("product", "emission_category"))) |>
  filter(!is.na(emission_category)) |>
  distinct()
```

```{r, results='asis'}
cat("Distinct europages products:", n_distinct(matched_ecoinvent$product))
```

### Distinct europages products that have `sector_target` 

#### Input

```{r, echo=FALSE}
example_sector_profile <- example_transition_risk_sector_ep_product_des_analysis()
kable(example_sector_profile)
```

#### Output

```{r, echo=FALSE}
products_sector_target <- example_sector_profile |>
  select(all_of(c("product", "sector_target"))) |>
  filter(!is.na(sector_target)) |>
  distinct()
```

```{r, results='asis'}
cat("Distinct europages products:", n_distinct(products_sector_target$product))
```

### Average amount of distinct ep products per company for emission profile if the company have atleast one matched ecoinvent product

```{r}
avg_distinct_products_per_company_atleast_one_matched_ecoinvent <- function(data, col) {
  companies_with_atleast_one_matched_product <- data |>
    select(all_of(c("companies_id", "product", col))) |>
    filter(!is.na(.data[[col]])) |>
    distinct()
  result <- data |>
    select(all_of(c("companies_id", "product"))) |>
    filter(companies_id %in% companies_with_atleast_one_matched_product$companies_id) |>
    mutate(distinct_products_per_company = n_distinct(product, na.rm = TRUE), .by = "companies_id") |>
    select(-all_of(c("product"))) |>
    distinct()
  
  sum(result$distinct_products_per_company) / n_distinct(result$companies_id)
}
```

```{r, results='asis'}
cat("Average amount of distinct ep products per company for emission profile if the company have atleast one matched ecoinvent product:", avg_distinct_products_per_company_atleast_one_matched_ecoinvent(example_emission_profile, "emission_category"))
```

### Average amount of ep distinct products per company for sector profile if the company have atleast one product with sector target

```{r, results='asis'}
cat("Average amount of distinct ep products per company for sector profile if the company have atleast one product with sector target:", avg_distinct_products_per_company_atleast_one_matched_ecoinvent(example_sector_profile, "sector_category"))
```

### Average amount of distinct ep products per company for transition risk profile if the company have atleast one product with transition risk category

#### Input

```{r, echo=FALSE}
example_transition_risk_profile <- example_transition_risk_ep_product_des_analysis()
kable(example_transition_risk_profile)
```

```{r, results='asis'}
cat("Average amount of distinct ep products per company for sector profile if the company have atleast one product with transition risk category:", avg_distinct_products_per_company_atleast_one_matched_ecoinvent(example_transition_risk_profile, "transition_risk_category"))
```

### Average amount of distinct ep products per company

```{r, echo=FALSE}
avg_distinct_products_per_company <- function(data) {
  result <- data |>
    select(all_of(c("companies_id", "product"))) |>
    mutate(distinct_products_per_company = n_distinct(product, na.rm = TRUE), .by = "companies_id") |>
    select(-all_of(c("product"))) |>
    distinct()
  
  sum(result$distinct_products_per_company) / n_distinct(result$companies_id)
}
```

```{r, results='asis'}
cat("Average amount of distinct ep products per company: ", avg_distinct_products_per_company(example_transition_risk_profile))
```

### Distinct ep products without a risk category for emission, sector, and transition risk profile

```{r, echo=FALSE}
distinct_products_without_risk_category <- function(data, profile) {
  result <- data |>
    select(all_of(c("product", profile))) |>
    distinct() |>
    filter(is.na(.data[[profile]]))
  
  n_distinct(result$product)
}
```

```{r, results='asis'}
cat("Distinct ep products without a risk category for emission profile:", distinct_products_without_risk_category(example_emission_profile, "emission_category"))
cat("Distinct ep products without a risk category for sector profile:", distinct_products_without_risk_category(example_sector_profile, "sector_category"))
cat("Distinct ep products without a risk category for transition risk profile:", distinct_products_without_risk_category(example_transition_risk_profile, "transition_risk_category"))
```

### Average profile ranking of all ep products per grouping_emission

#### Input

```{r, echo=FALSE}
transition_risk_product <- product_transition_risk
profile_rank_df <- transition_risk_product |>
  select(all_of(c("product", "grouping_emission", "emission_rank"))) |> 
  filter(grouping_emission %in% c("all", "tilt_subsector")) |>
  distinct() |>
  filter(product %in% c("tent", "surface engineering"))
```

```{r, results='asis', echo=FALSE}
kable(profile_rank_df |> head(10))
```

#### Output

```{r}
avg_profile_ranking_df <- profile_rank_df |>
  mutate(sum_profile_ranking = sum(.data$emission_rank, na.rm = TRUE), .by = "grouping_emission") |>
  mutate(distinct_products_per_benchmark = n_distinct(.data$product, na.rm = TRUE), .by = "grouping_emission") |>
  mutate("emission rank average" = sum_profile_ranking/distinct_products_per_benchmark) |>
  select(-all_of(c("sum_profile_ranking", "distinct_products_per_benchmark", "emission_rank", "product"))) |>
  distinct()
```

```{r, results='asis', echo=FALSE}
kable(avg_profile_ranking_df, align = "lc", caption = "Average profile ranking of all ep products per grouping_emission", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(1:2, width = "4cm")
```

### Average reduction targets of all ep products per grouping_sector

#### Input

```{r, echo=FALSE}
reduction_targets_df <- transition_risk_product |>
  select(all_of(c("product", "scenario", "year", "sector_target"))) |>
  distinct() |>
  mutate(grouping_sector = paste(.data$scenario, .data$year, sep = "_")) |>
  select(-all_of(c("scenario", "year"))) |>
  filter(product %in% c("tent", "surface engineering"))
```

```{r, echo=FALSE}
kable(reduction_targets_df |> head(10))
```

#### Output

```{r, echo=FALSE}
avg_reduction_targets_df <- reduction_targets_df |>
  mutate(sum_reduction_targets = sum(.data$sector_target, na.rm = TRUE), .by = "grouping_sector") |>
  mutate(distinct_products_per_scenario_year = n_distinct(.data$product, na.rm = TRUE), .by = "grouping_sector") |>
  mutate("sector target average" = sum_reduction_targets/distinct_products_per_scenario_year) |>
  select(-all_of(c("sum_reduction_targets", "distinct_products_per_scenario_year", "sector_target", "product"))) |>
  distinct() |>
  filter(!str_detect(grouping_sector, "NA"))
```

```{r, results='asis', echo=FALSE}
kable(avg_reduction_targets_df, align = "lc", caption = "Average reduction targets of all ep products per grouping_sector", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(1:2, width = "4cm")
```

### Average transition risk scores of all ep products per tilt_subsector benchmarks

#### Input

```{r, echo=FALSE}
trs_df <- transition_risk_product |>
  select(all_of(c("product", "grouping_transition_risk", "transition_risk_score"))) |>
  distinct() |>
  filter(grouping_transition_risk %in% c("1.5C RPS_2030_tilt_subsector", "1.5C RPS_2050_tilt_subsector",
                                         "NZ 2050_2030_tilt_subsector", "NZ 2050_2050_tilt_subsector",
                                         "1.5C RPS_2030_all", "1.5C RPS_2050_all",
                                         "NZ 2050_2030_all", "NZ 2050_2050_all")) |>
  filter(product %in% c("tent", "surface engineering"))
```

```{r, results='asis', echo=FALSE}
kable(trs_df |> head(10))
```

#### Output

```{r, echo=FALSE}
avg_trs_df <- trs_df |>
  mutate(sum_trs = sum(.data$transition_risk_score, na.rm = TRUE), .by = "grouping_transition_risk") |>
  mutate(distinct_products_per_benchmark = n_distinct(.data$product, na.rm = TRUE), .by = "grouping_transition_risk") |>
  mutate("transition risk average" = sum_trs/distinct_products_per_benchmark) |>
  select(-all_of(c("sum_trs", "distinct_products_per_benchmark", "transition_risk_score", "product"))) |>
  distinct()

avg_trs_df$group <- sub(".*0_", "", avg_trs_df$grouping_transition_risk)
avg_trs_df$scenario <- sub("(0)_.*", "\\1", avg_trs_df$grouping_transition_risk)
avg_trs_df <- avg_trs_df |>
  select(-all_of(c("grouping_transition_risk"))) |>
  relocate(all_of(c("group", "scenario")))
```

```{r, results='asis', echo=FALSE}
kable(avg_trs_df, align = "llc", caption = "Average transition risk scores of all ep products per transition risk groups", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(1, width = "3cm") |>
  column_spec(3, width = "5cm") |>
  collapse_rows(columns = 1, valign = "top")
```

### Average NA share per company 

#### Companies with atleast one matched ecoinvent product for emission profile

```{r, echo = FALSE}
# read_csv("transition_risk_profile_at_company_level_all_countries_wide_21_08_24.csv")
transition_risk_company <- company_transition_risk
companies_atleast_one_product_per_profile <- function(data, profile) {
  data |>
    select(all_of(c("companies_id", "product", profile))) |>
    filter(!is.na(.data[[profile]])) |>
    distinct()
}
```

```{r, results='asis', echo=FALSE}
companies_atleast_one_product_emission_profile <- companies_atleast_one_product_per_profile(transition_risk_product, "emission_category")
kable(companies_atleast_one_product_emission_profile |> head(10))
```

#### Average NA share per company which have atleast one matched ecoinvent product for emission profile

```{r, echo=FALSE}
na_emission_profile <- transition_risk_company |>
  select(all_of(c("companies_id", "emission_category_NA"))) |>
  distinct() |>
  filter(companies_id %in% companies_atleast_one_product_emission_profile$companies_id)

kable(na_emission_profile |> head(10))
```

```{r, echo=FALSE}
average_na_emission_profile <- sum(na_emission_profile$emission_category_NA, na.rm = TRUE) / n_distinct(na_emission_profile$companies_id)
```

```{r, results='asis'}
cat("Average NA share per company with atleast one matched ecoinvent product for emission profile:", average_na_emission_profile)
```

#### Companies with atleast one product with sector category/sector target

```{r, results='asis', echo=FALSE}
companies_atleast_one_product_sector_profile <- companies_atleast_one_product_per_profile(transition_risk_product, "sector_category")
kable(companies_atleast_one_product_emission_profile |> head(10))
```

#### Average NA share per company which have atleast one product with sector category

```{r, echo=FALSE}
na_sector_profile <- transition_risk_company |>
  select(all_of(c("companies_id", "sector_category_NA"))) |>
  distinct() |>
  filter(companies_id %in% companies_atleast_one_product_sector_profile$companies_id)

kable(na_sector_profile |> head(10))
```

```{r, echo=FALSE}
average_na_sector_profile <- sum(na_sector_profile$sector_category_NA, na.rm = TRUE) / n_distinct(na_sector_profile$companies_id)
```

```{r, results='asis'}
cat("Average NA share per company with atleast one product with sector category:", average_na_sector_profile)
```

#### Companies with atleast one product with transition risk category

```{r, results='asis', echo=FALSE}
companies_atleast_one_product_transition_risk_profile <- companies_atleast_one_product_per_profile(transition_risk_product, "transition_risk_category")
kable(companies_atleast_one_product_transition_risk_profile |> head(10))
```

#### Average NA share per company which have atleast one product with transition risk category

```{r, echo=FALSE}
na_transition_risk_profile <- transition_risk_company |>
  select(all_of(c("companies_id", "transition_risk_NA_share"))) |>
  distinct() |>
  filter(companies_id %in% companies_atleast_one_product_transition_risk_profile$companies_id)

kable(na_transition_risk_profile |> head(10))
```

```{r, echo=FALSE}
average_na_transition_risk_profile <- sum(na_transition_risk_profile$transition_risk_NA_share, na.rm = TRUE) / n_distinct(na_transition_risk_profile$companies_id)
```

```{r, results='asis'}
cat("Average NA share per company with atleast one product with transition risk category:", average_na_transition_risk_profile)
```
