---
title: "Descriptive analysis of transition risk scores for all tilt_subsectors per scenario-year-tilt_subsector benchmark"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This article shows how to calculate the descriptive analysis of transition risk 
scores for all `tilt_subsectors` per scenario-year-tilt_subsector benchmark 
using product-level output of Transition risk profile indicator.

```{r setup, warning=FALSE, echo = FALSE, message=FALSE}
library(tiltDataAnalysis)
library(kableExtra)
library(dplyr)
library(knitr)
options(readr.show_col_types = FALSE)
```

### Example subset of product-level output of Transition risk profile.

```{r}
transition_risk_product_example <- example_transition_risk_product_trs_des_analysis()
kable(transition_risk_product_example |> head(20))
```

### Descriptive analysis for benchmark "1.5C RPS_2030_tilt_subsector"

```{r}
ipr_2030 <- calculate_trs_descriptive_analysis_per_tr_benchmark(
   transition_risk_product_example,
   "1.5C RPS_2030_tilt_subsector"
 )

kable(ipr_2030, align = "llcccc", caption = "Descriptive analysis for benchmark 1.5C RPS_2030_tilt_subsector", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(3:6, width = "2.5cm")
```

### Descriptive analysis for benchmark "1.5C RPS_2050_tilt_subsector"

```{r}
ipr_2050 <- calculate_trs_descriptive_analysis_per_tr_benchmark(
   transition_risk_product_example,
   "1.5C RPS_2050_tilt_subsector"
 )

kable(ipr_2050, align = "llcccc", caption = "Descriptive analysis for benchmark 1.5C RPS_2050_tilt_subsector", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(3:6, width = "2.5cm")
```

### Descriptive analysis for benchmark "NZ 2050_2030_tilt_subsector"

```{r}
weo_2030 <- calculate_trs_descriptive_analysis_per_tr_benchmark(
   transition_risk_product_example,
   "NZ 2050_2030_tilt_subsector"
 )

kable(weo_2030, align = "llcccc", caption = "Descriptive analysis for benchmark NZ 2050_2030_tilt_subsector", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(3:6, width = "2.5cm")
```

### Descriptive analysis for benchmark "NZ 2050_2050_tilt_subsector"

```{r}
weo_2050 <- calculate_trs_descriptive_analysis_per_tr_benchmark(
   transition_risk_product_example,
   "NZ 2050_2050_tilt_subsector"
 )

kable(weo_2050, align = "llcccc", caption = "Descriptive analysis for benchmark NZ 2050_2050_tilt_subsector", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(3:6, width = "2.5cm")
```
