---
title: "Descriptive analysis of best case and worst case for emission profile"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This article shows how to calculate the descriptive analysis of equal weight,
best case, and worst case for emission profile.

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
devtools::load_all(".")
library(kableExtra)
library(dplyr)
library(knitr)
library(ggplot2)
options(readr.show_col_types = FALSE)
```

### Example product-level output of emission profile for best case and worst case

```{r, warning=FALSE}
emission_product_example <- example_emission_product_best_case_worst_case()
kable(emission_product_example)
```

### Average `emissions_profile_equal_weight` per benchmark and emission_profile

```{r, warning=FALSE}
avg_per_benchmark_risk_category <- function(data, col) {
  data |>
    select(all_of(c("benchmark", "emission_profile", col))) |>
    summarise(total_mode = sum(.data[[col]], na.rm = TRUE), .by = c("benchmark", "emission_profile")) |>
    mutate(proportion = total_mode / sum(total_mode), .by = c("benchmark")) |>
    select(-all_of(c("total_mode"))) |>
    distinct()
}
avg_emission_profile_equal_weight_per_benchmark_risk_category <- avg_per_benchmark_risk_category(emission_product_example, "emissions_profile_equal_weight") |>
  rename("Average `emissions_profile_equal_weight`" = "proportion")

kable(avg_emission_profile_equal_weight_per_benchmark_risk_category)
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
score_colors <- function(...) c("low" = "#F6CB4E", "medium" = "#B3D15D", "high" = "#E3693B")
fill_score_colors <- function() scale_fill_manual(values = score_colors(), na.value = "#0476D0")

plot_bar_plot_profile <- function(data, col) {
  ggplot(data, aes(x = .data[[col]], y = .data$benchmark, fill = .data$emission_profile)) +
    geom_col(position = position_stack(reverse = TRUE), width = 0.5) +
    fill_score_colors() +
    tiltPlot::theme_tiltplot() +
    xlim(0, NA)
}

plot_bar_plot_profile(avg_emission_profile_equal_weight_per_benchmark_risk_category, "Average `emissions_profile_equal_weight`") +
  labs(title = "Average `emissions_profile_equal_weight` \n per benchmark and emission_profile")
```

### Average `emissions_profile_best_case` per benchmark and emission_profile

```{r, warning=FALSE}
avg_emission_profile_best_case_per_benchmark_risk_category <- avg_per_benchmark_risk_category(emission_product_example, "emissions_profile_best_case") |>
  rename("Average `emissions_profile_best_case`" = "proportion")

kable(avg_emission_profile_best_case_per_benchmark_risk_category)
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_emission_profile_best_case_per_benchmark_risk_category, "Average `emissions_profile_best_case`") +
  labs(title = "Average `emissions_profile_best_case` \n per benchmark and emission_profile")
```

### Average `emissions_profile_worst_case` per benchmark and emission_profile

```{r, warning=FALSE}
avg_emission_profile_worst_case_per_benchmark_risk_category <- avg_per_benchmark_risk_category(emission_product_example, "emissions_profile_worst_case") |>
  rename("Average `emissions_profile_worst_case`" = "proportion")

kable(avg_emission_profile_worst_case_per_benchmark_risk_category)
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_emission_profile_worst_case_per_benchmark_risk_category, "Average `emissions_profile_worst_case`") +
  labs(title = "Average `emissions_profile_worst_case` \n per benchmark and emission_profile")
```

### Average `emissions_profile_equal_weight` per benchmark and emission_profile for a country

```{r, warning=FALSE}
avg_per_benchmark_country_risk_category <- function(data, col, country_value) {
  data |>
    select(all_of(c("benchmark", "country", "emission_profile", col))) |>
    filter(country == country_value) |>
    summarise(total_mode = sum(.data[[col]], na.rm = TRUE), .by = c("benchmark", "emission_profile")) |>
    mutate(proportion = total_mode / sum(total_mode), .by = c("benchmark")) |>
    select(-all_of(c("total_mode"))) |>
    distinct()
}
avg_emission_profile_equal_weight_per_benchmark_country_risk_category <- avg_per_benchmark_country_risk_category(emission_product_example, "emissions_profile_equal_weight", "france") |>
  rename("Average `emissions_profile_equal_weight`" = "proportion")

kable(avg_emission_profile_equal_weight_per_benchmark_country_risk_category)
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_emission_profile_equal_weight_per_benchmark_country_risk_category, "Average `emissions_profile_equal_weight`") +
  labs(title = "Average `emissions_profile_equal_weight` \n per benchmark and emission_profile for country `France`")
```

### Average `emissions_profile_base_case` per benchmark and emission_profile for a country

```{r, warning=FALSE}
avg_emission_profile_best_case_per_benchmark_country_risk_category <- avg_per_benchmark_country_risk_category(emission_product_example, "emissions_profile_best_case", "france") |>
  rename("Average `emissions_profile_best_case`" = "proportion")

kable(avg_emission_profile_best_case_per_benchmark_country_risk_category)
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_emission_profile_best_case_per_benchmark_country_risk_category, "Average `emissions_profile_best_case`") +
  labs(title = "Average `emissions_profile_best_case` \n per benchmark and emission_profile for country `France`")
```

### Average `emissions_profile_worst_case` per benchmark and emission_profile for a country

```{r, warning=FALSE}
avg_emission_profile_worst_case_per_benchmark_country_risk_category <- avg_per_benchmark_country_risk_category(emission_product_example, "emissions_profile_worst_case", "france") |>
  rename("Average `emissions_profile_worst_case`" = "proportion")

kable(avg_emission_profile_worst_case_per_benchmark_country_risk_category)
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_emission_profile_worst_case_per_benchmark_country_risk_category, "Average `emissions_profile_worst_case`") +
  labs(title = "Average `emissions_profile_worst_case` \n per benchmark and emission_profile for country `France`")
```

### Example company-level output of transition risk profile for best case and worst case

```{r, warning=FALSE}
transition_risk_company_example <- example_transition_risk_company_emission_avg_best_case_worst_case()
kable(transition_risk_company_example)
```

### Descriptive analysis of `emission_rank_avg_equal_weight` per benchmark

```{r, warning=FALSE}
emission_rank_avg_per_benchmark <- function(data, col) {
  data |>
    select(all_of(c("companies_id", "grouping_emission", col))) |>
    distinct() |>
    mutate(sum_mode = sum(.data[[col]], na.rm = TRUE), .by = "grouping_emission") |>
    mutate(distinct_comp = n_distinct(companies_id, na.rm = TRUE), .by = "grouping_emission") |>
    mutate(average = sum_mode / distinct_comp) |>
    mutate(median = median(.data[[col]], na.rm = TRUE), .by = "grouping_emission") |>
    mutate("25th_quantile" = quantile(.data[[col]], 0.25, na.rm = TRUE), .by = "grouping_emission") |>
    mutate("75th_quantile" = quantile(.data[[col]], 0.75, na.rm = TRUE), .by = "grouping_emission") |>
    select(-all_of(c("sum_mode", col, "companies_id", "distinct_comp"))) |>
    distinct()
}
emission_rank_avg_equal_weight_per_benchmark <- emission_rank_avg_per_benchmark(transition_risk_company_example, "emission_rank_avg_equal_weight") 

kable(emission_rank_avg_equal_weight_per_benchmark, align = "lcccc", caption = "Descriptive analysis of `emission_rank_avg_equal_weight` per grouping_emission", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(5, width = "3cm") |>
  add_header_above(c(" ", "emission_rank_avg_equal_weight" = 4))
```

### Descriptive analysis of `emission_rank_avg_best_case` per benchmark

```{r, warning=FALSE}
emission_rank_avg_best_case_per_benchmark <- emission_rank_avg_per_benchmark(transition_risk_company_example, "emission_rank_avg_best_case")

kable(emission_rank_avg_best_case_per_benchmark, align = "lcccc", caption = "Descriptive analysis of `emission_rank_avg_best_case` per grouping_emission", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(5, width = "3cm") |>
  add_header_above(c(" ", "emission_rank_avg_best_case" = 4))
```

### Descriptive analysis of `emission_rank_avg_worst_case` per benchmark

```{r, warning=FALSE}
emission_rank_avg_worst_case_per_benchmark <- emission_rank_avg_per_benchmark(transition_risk_company_example, "emission_rank_avg_worst_case")

kable(emission_rank_avg_worst_case_per_benchmark, align = "lcccc", caption = "Descriptive analysis of `emission_rank_avg_worst_case` per grouping_emission", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(5, width = "3cm") |>
  add_header_above(c(" ", "emission_rank_avg_worst_case" = 4))
```

### Descriptive analysis of `emission_rank_avg_equal_weight` per benchmark for a country

```{r, warning=FALSE}
emission_rank_avg_per_benchmark_country <- function(data, col, country_value) {
  data |>
    select(all_of(c("country", "companies_id", "grouping_emission", col))) |>
    distinct() |>
    filter(country == country_value) |>
    mutate(sum_mode = sum(.data[[col]], na.rm = TRUE), .by = "grouping_emission") |>
    mutate(distinct_comp = n_distinct(companies_id, na.rm = TRUE), .by = "grouping_emission") |>
    mutate(average = sum_mode / distinct_comp, .by = "grouping_emission") |>
    mutate(median = median(.data[[col]], na.rm = TRUE), .by = "grouping_emission") |>
    mutate("25th_quantile" = quantile(.data[[col]], 0.25, na.rm = TRUE), .by = "grouping_emission") |>
    mutate("75th_quantile" = quantile(.data[[col]], 0.75, na.rm = TRUE), .by = "grouping_emission") |>
    select(-all_of(c("sum_mode", col, "companies_id", "distinct_comp"))) |>
    distinct()
}
emission_rank_avg_equal_weight_per_benchmark_country <- emission_rank_avg_per_benchmark_country(transition_risk_company_example, "emission_rank_avg_equal_weight", "france") 

kable(emission_rank_avg_equal_weight_per_benchmark_country, align = "llcccc", caption = "Descriptive analysis of `emission_rank_avg_equal_weight` per grouping_emission for country `France`", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(6, width = "3cm") |>
  add_header_above(c(" ", " ", "emission_rank_avg_equal_weight" = 4))
```

### Descriptive analysis of `emission_rank_avg_best_case` per benchmark for a country

```{r, warning=FALSE}
emission_rank_avg_best_case_per_benchmark_country <- emission_rank_avg_per_benchmark_country(transition_risk_company_example, "emission_rank_avg_best_case", "france")

kable(emission_rank_avg_best_case_per_benchmark_country, align = "llcccc", caption = "Descriptive analysis of `emission_rank_avg_best_case` per grouping_emission for country `France`", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(6, width = "3cm") |>
  add_header_above(c(" ", " ", "emission_rank_avg_best_case" = 4))
```

### Descriptive analysis of `emission_rank_avg_best_case` per benchmark for a country

```{r, warning=FALSE}
emission_rank_avg_worst_case_per_benchmark_country <- emission_rank_avg_per_benchmark_country(transition_risk_company_example, "emission_rank_avg_worst_case", "france")

kable(emission_rank_avg_worst_case_per_benchmark_country, align = "llcccc", caption = "Descriptive analysis of `emission_rank_avg_worst_case` per grouping_emission for country `France`", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(6, width = "3cm") |>
  add_header_above(c(" ", " ", "emission_rank_avg_worst_case" = 4))
```
