---
title: "Descriptive analysis of best case and worst case for transition risk profile"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This article shows how to calculate the descriptive analysis of equal weight,
best case, and worst case for transition risk profile.

```{r setup, echo = FALSE, message=FALSE}
library(tiltDataAnalysis)
library(dplyr)
library(knitr)
library(ggplot2)
options(readr.show_col_types = FALSE)
options(width = 5000)
```

### Example product-level output of transition risk profile for equal weight, best case, and worst case

```{r, warning=FALSE}
transition_risk_product_example <- example_transition_risk_product_best_case_worst_case()
kable(transition_risk_product_example)
```

### Average `transition_risk_profile_equal_weight` per `grouping_transition_risk` and `transition_risk_category`

```{r, warning=FALSE}
avg_per_benchmark_risk_category <- function(data, col) {
  data |>
    select(all_of(c("grouping_transition_risk", "transition_risk_category", col))) |>
    distinct() |>
    summarise(total_mode = sum(.data[[col]], na.rm = TRUE), .by = c("grouping_transition_risk", "transition_risk_category")) |>
    mutate(proportion = total_mode / sum(total_mode), .by = c("grouping_transition_risk")) |>
    select(-all_of(c("total_mode"))) |>
    distinct()
}
avg_transition_risk_equal_weight_per_benchmark_risk_category <- avg_per_benchmark_risk_category(transition_risk_product_example, "transition_risk_profile_equal_weight") |>
  rename(avg_equal_weight = "proportion")

kable(avg_transition_risk_equal_weight_per_benchmark_risk_category)
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
score_colors <- function(...) c("low" = "#F6CB4E", "medium" = "#B3D15D", "high" = "#E3693B")
fill_score_colors <- function() scale_fill_manual(values = score_colors(), na.value = "#0476D0")

plot_bar_plot_profile <- function(data, col) {
  ggplot(data, aes(x = .data[[col]], y = .data$grouping_transition_risk, fill = .data$transition_risk_category)) +
    geom_col(position = position_stack(reverse = TRUE), width = 0.5) +
    fill_score_colors() +
    tiltPlot::theme_tiltplot() +
    xlim(0, NA)
}

plot_bar_plot_profile(avg_transition_risk_equal_weight_per_benchmark_risk_category, "avg_equal_weight")
```

### Average `transition_risk_profile_best_case` per per `grouping_transition_risk` and `transition_risk_category`

```{r, warning=FALSE}
avg_transition_risk_best_case_per_benchmark_risk_category <- avg_per_benchmark_risk_category(transition_risk_product_example, "transition_risk_profile_best_case") |>
  rename(avg_best_case = "proportion")

kable(avg_transition_risk_best_case_per_benchmark_risk_category)
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_transition_risk_best_case_per_benchmark_risk_category, "avg_best_case")
```

### Average `transition_risk_profile_worst_case` per per `grouping_transition_risk` and `transition_risk_category`

```{r, warning=FALSE}
avg_transition_risk_worst_case_per_benchmark_risk_category <- avg_per_benchmark_risk_category(transition_risk_product_example, "transition_risk_profile_worst_case") |>
  rename(avg_worst_case = "proportion")

kable(avg_transition_risk_worst_case_per_benchmark_risk_category)
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_transition_risk_worst_case_per_benchmark_risk_category, "avg_worst_case")
```

### Average `transition_risk_profile_equal_weight` per `grouping_transition_risk` and `transition_risk_category` for a country

```{r, warning=FALSE}
avg_per_benchmark_country_risk_category <- function(data, col, country_value) {
  data |>
    select(all_of(c("grouping_transition_risk", "country", "transition_risk_category", col))) |>
    distinct() |>
    filter(country == country_value) |>
    summarise(total_mode = sum(.data[[col]], na.rm = TRUE), .by = c("grouping_transition_risk", "transition_risk_category")) |>
    mutate(proportion = total_mode / sum(total_mode), .by = c("grouping_transition_risk")) |>
    select(-all_of(c("total_mode"))) |>
    distinct()
}
avg_transition_risk_equal_weight_per_benchmark_country_risk_category <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_equal_weight", "france") |>
  rename(avg_equal_weight = "proportion")

kable(avg_transition_risk_equal_weight_per_benchmark_country_risk_category)
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_transition_risk_equal_weight_per_benchmark_country_risk_category, "avg_equal_weight")
```

### Average `transition_risk_profile_best_case` per `grouping_transition_risk` and `transition_risk_category` for a country

```{r, warning=FALSE}
avg_transition_risk_best_case_per_benchmark_country_risk_category <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_best_case", "france") |>
  rename(avg_best_case = "proportion")

kable(avg_transition_risk_best_case_per_benchmark_country_risk_category)
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_transition_risk_best_case_per_benchmark_country_risk_category, "avg_best_case")
```

### Average `transition_risk_profile_worst_case` per `grouping_transition_risk` and `transition_risk_category` for a country

```{r, warning=FALSE}
avg_transition_risk_worst_case_per_benchmark_country_risk_category <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_worst_case", "france") |>
  rename(avg_worst_case = "proportion")

kable(avg_transition_risk_worst_case_per_benchmark_country_risk_category)
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_transition_risk_worst_case_per_benchmark_country_risk_category, "avg_worst_case")
```

### Example company-level output of transition risk profile for best case and worst case

```{r, warning=FALSE}
transition_risk_company_example <- example_transition_risk_company_transition_risk_avg_best_case_worst_case()
kable(transition_risk_company_example)
```

### Descriptive analysis of `avg_transition_risk_equal_weight` per `grouping_transition_risk`

```{r, warning=FALSE}
avg_transition_risk_per_benchmark <- function(data, col) {
  data |>
    select(all_of(c("companies_id", "grouping_transition_risk", col))) |>
    distinct() |>
    mutate(sum_mode = sum(.data[[col]], na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate(distinct_comp = n_distinct(companies_id, na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate(average = sum_mode / distinct_comp) |>
    mutate(rank_median = median(.data[[col]], na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate(rank_25th = quantile(.data[[col]], 0.25, na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate(rank_75th = quantile(.data[[col]], 0.75, na.rm = TRUE), .by = "grouping_transition_risk") |>
    select(-all_of(c("sum_mode", col, "companies_id", "distinct_comp"))) |>
    distinct()
}
avg_transition_risk_equal_weight_per_benchmark <- avg_transition_risk_per_benchmark(transition_risk_company_example, "avg_transition_risk_equal_weight") |>
  rename("average_avg_transition_risk_equal_weight" = "average",
         "median_avg_transition_risk_equal_weight" = "rank_median",
         "25th_quantile_avg_transition_risk_equal_weight" = "rank_25th",
         "75th_quantile_avg_transition_risk_equal_weight" = "rank_75th")

kable(avg_transition_risk_equal_weight_per_benchmark)
```

### Descriptive analysis of `avg_transition_risk_best_case` per `grouping_transition_risk`

```{r, warning=FALSE}
avg_transition_risk_best_case_per_benchmark <- avg_transition_risk_per_benchmark(transition_risk_company_example, "avg_transition_risk_best_case") |>
  rename("average_avg_transition_risk_best_case" = "average",
         "median_avg_transition_risk_best_case" = "rank_median",
         "25th_quantile_avg_transition_risk_best_case" = "rank_25th",
         "75th_quantile_avg_transition_risk_best_case" = "rank_75th")

kable(avg_transition_risk_best_case_per_benchmark)
```

### Descriptive analysis of `avg_transition_risk_worst_case` per `grouping_transition_risk`

```{r, warning=FALSE}
avg_transition_risk_worst_case_per_benchmark <- avg_transition_risk_per_benchmark(transition_risk_company_example, "avg_transition_risk_worst_case") |>
  rename("average_avg_transition_risk_worst_case" = "average",
         "median_avg_transition_risk_worst_case" = "rank_median",
         "25th_quantile_avg_transition_risk_worst_case" = "rank_25th",
         "75th_quantile_avg_transition_risk_worst_case" = "rank_75th")

kable(avg_transition_risk_worst_case_per_benchmark)
```

### Descriptive analysis of `avg_transition_risk_equal_weight` per `grouping_transition_risk` for a country

```{r, warning=FALSE}
avg_transition_risk_per_benchmark_country <- function(data, col, country_value) {
  data |>
    select(all_of(c("companies_id", "grouping_transition_risk", "country", col))) |>
    distinct() |>
    filter(country == country_value) |>
    mutate(sum_mode = sum(.data[[col]], na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate(distinct_comp = n_distinct(companies_id, na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate(average = sum_mode / distinct_comp) |>
    mutate(rank_median = median(.data[[col]], na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate(rank_25th = quantile(.data[[col]], 0.25, na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate(rank_75th = quantile(.data[[col]], 0.75, na.rm = TRUE), .by = "grouping_transition_risk") |>
    select(-all_of(c("sum_mode", col, "companies_id", "distinct_comp"))) |>
    distinct()
}
avg_transition_risk_equal_weight_per_benchmark_country  <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_equal_weight", "france") |>
  rename("average_avg_transition_risk_equal_weight" = "average",
         "median_avg_transition_risk_equal_weight" = "rank_median",
         "25th_quantile_avg_transition_risk_equal_weight" = "rank_25th",
         "75th_quantile_avg_transition_risk_equal_weight" = "rank_75th")

kable(avg_transition_risk_equal_weight_per_benchmark_country)
```

### Descriptive analysis of `avg_transition_risk_best_case` per `grouping_transition_risk` for a country

```{r, warning=FALSE}
avg_transition_risk_best_case_per_benchmark_country  <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_best_case", "france") |>
  rename("average_avg_transition_risk_best_case" = "average",
         "median_avg_transition_risk_best_case" = "rank_median",
         "25th_quantile_avg_transition_risk_best_case" = "rank_25th",
         "75th_quantile_avg_transition_risk_best_case" = "rank_75th")

kable(avg_transition_risk_best_case_per_benchmark_country)
```

### Descriptive analysis of `avg_transition_risk_worst_case` per `grouping_transition_risk` for a country

```{r, warning=FALSE}
avg_transition_risk_worst_case_per_benchmark_country  <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_worst_case", "france") |>
  rename("average_avg_transition_risk_worst_case" = "average",
         "median_avg_transition_risk_worst_case" = "rank_median",
         "25th_quantile_avg_transition_risk_worst_case" = "rank_25th",
         "75th_quantile_avg_transition_risk_worst_case" = "rank_75th")

kable(avg_transition_risk_worst_case_per_benchmark_country)
```
