---
title: "Descriptive analysis of best case and worst case for transition risk profile"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Roboto+Condensed:wght@400;700&display=swap');

table {
  font-family: 'Roboto Condensed', sans-serif;
}
```

This article shows how to calculate the descriptive analysis of equal weight,
best case, and worst case for transition risk profile.

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
library(tiltDataAnalysis)
library(stringr)
library(dplyr)
library(knitr)
library(ggplot2)
library(kableExtra)
options(readr.show_col_types = FALSE)
```

### Example product-level output of transition risk profile for equal weight, best case, and worst case

```{r, warning=FALSE, echo=FALSE}
# read_csv("transition_risk_profile_at_product_level_all_countries_wide_22_08_24.csv")
transition_risk_product_example <- example_transition_risk_product_best_case_worst_case()
kable(transition_risk_product_example |> head(20))
```

### Average `transition_risk_profile_equal_weight` per `grouping_transition_risk` and `transition_risk_category`

```{r, warning=FALSE, echo=FALSE}
avg_per_benchmark_risk_category <- function(data, col) {
  data |>
    select(all_of(c("grouping_transition_risk", "transition_risk_category", col))) |>
    summarise(total_mode = sum(.data[[col]], na.rm = TRUE), .by = c("grouping_transition_risk", "transition_risk_category")) |>
    mutate(proportion = total_mode / sum(total_mode), .by = c("grouping_transition_risk")) |>
    select(-all_of(c("total_mode"))) |>
    distinct() |>
    filter(str_detect(grouping_transition_risk, "all|tilt_subsector")) |>
    filter(!str_detect(grouping_transition_risk, "NA|unit")) |>
    arrange(grouping_transition_risk)
}
avg_transition_risk_equal_weight_per_benchmark_risk_category <- avg_per_benchmark_risk_category(transition_risk_product_example, "transition_risk_profile_equal_weight") |>
  rename("Average `transition_risk_profile_equal_weight`" = "proportion")
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
score_colors <- function(...) c("low" = "#F6CB4E", "medium" = "#B3D15D", "high" = "#E3693B")
fill_score_colors <- function() scale_fill_manual(values = score_colors(), na.value = "#0476D0")

plot_bar_plot_profile <- function(data, col) {
  data <- data |>
  mutate(grouping_transition_risk = factor(grouping_transition_risk, levels = c(
    grep("_subsector", unique(grouping_transition_risk), value = TRUE),
    grep("_all", unique(grouping_transition_risk), value = TRUE)
  )))

  ggplot(data, aes(x = .data[[col]], y = .data$grouping_transition_risk, fill = .data$transition_risk_category)) +
    geom_col(position = position_stack(reverse = TRUE), width = 0.5) +
    fill_score_colors() +
    tiltPlot::theme_tiltplot() +
    xlim(0, NA)
}

plot_bar_plot_profile(avg_transition_risk_equal_weight_per_benchmark_risk_category, "Average `transition_risk_profile_equal_weight`") +
  labs(x = "Average transition risk category \n under equal weight assumption", y = "Group", title = "Average transition risk category under \n equal weight assumption per \n grouping_transition_risk and \n transition_risk_category", fill = "transition risk category")
```

### Average `transition_risk_profile_best_case` per per `grouping_transition_risk` and `transition_risk_category`

```{r, warning=FALSE, echo=FALSE}
avg_transition_risk_best_case_per_benchmark_risk_category <- avg_per_benchmark_risk_category(transition_risk_product_example, "transition_risk_profile_best_case") |>
  rename("Average `transition_risk_profile_best_case`" = "proportion")
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_transition_risk_best_case_per_benchmark_risk_category, "Average `transition_risk_profile_best_case`") +
  labs(x = "Average transition risk category \n under best case assumption", y = "Group", title = "Average transition risk category under \n best case assumption per \n grouping_transition_risk and \n transition_risk_category", fill = "transition risk category")
```

### Average `transition_risk_profile_worst_case` per per `grouping_transition_risk` and `transition_risk_category`

```{r, warning=FALSE, echo=FALSE}
avg_transition_risk_worst_case_per_benchmark_risk_category <- avg_per_benchmark_risk_category(transition_risk_product_example, "transition_risk_profile_worst_case") |>
  rename("Average `transition_risk_profile_worst_case`" = "proportion")
```

#### Bar plot

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_transition_risk_worst_case_per_benchmark_risk_category, "Average `transition_risk_profile_worst_case`") +
  labs(x = "Average transition risk category \n under worst case assumption", y = "Group", title = "Average transition risk category under \n worst case assumption per \n  grouping_transition_risk and \n transition_risk_category", fill = "transition risk category")
```

### Average `transition_risk_profile_equal_weight` per `grouping_transition_risk` and `transition_risk_category` for a country

```{r, warning=FALSE, echo=FALSE}
avg_per_benchmark_country_risk_category <- function(data, col, country_value) {
  data |>
    select(all_of(c("grouping_transition_risk", "country", "transition_risk_category", col))) |>
    filter(country == country_value) |>
    summarise(total_mode = sum(.data[[col]], na.rm = TRUE), .by = c("grouping_transition_risk", "transition_risk_category")) |>
    mutate(proportion = total_mode / sum(total_mode), .by = c("grouping_transition_risk")) |>
    select(-all_of(c("total_mode"))) |>
    distinct() |>
    filter(str_detect(grouping_transition_risk, "all|tilt_subsector")) |>
    filter(!str_detect(grouping_transition_risk, "NA|unit"))
}
avg_transition_risk_equal_weight_per_benchmark_country_risk_france <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_equal_weight", "france") |>
  rename("Average `transition_risk_profile_equal_weight`" = "proportion")
avg_transition_risk_equal_weight_per_benchmark_country_risk_austria <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_equal_weight", "austria") |>
  rename("Average `transition_risk_profile_equal_weight`" = "proportion")
avg_transition_risk_equal_weight_per_benchmark_country_risk_germany <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_equal_weight", "germany") |>
  rename("Average `transition_risk_profile_equal_weight`" = "proportion")
avg_transition_risk_equal_weight_per_benchmark_country_risk_netherlands <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_equal_weight", "netherlands") |>
  rename("Average `transition_risk_profile_equal_weight`" = "proportion")
avg_transition_risk_equal_weight_per_benchmark_country_risk_spain <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_equal_weight", "spain") |>
  rename("Average `transition_risk_profile_equal_weight`" = "proportion")
```

#### Bar plots

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_transition_risk_equal_weight_per_benchmark_country_risk_france, "Average `transition_risk_profile_equal_weight`") +
  labs(x = "Average transition risk category under \n equal weight assumption for France", y = "Group", title = "Average transition risk category under \n equal weight assumption per \n grouping_transition_risk and \n transition_risk_category for `france`", fill = "transition risk category")
plot_bar_plot_profile(avg_transition_risk_equal_weight_per_benchmark_country_risk_austria, "Average `transition_risk_profile_equal_weight`") +
  labs(x = "Average transition risk category under \n equal weight assumption for Austria", y = "Group", title = "Average transition risk category under \n equal weight assumption per \n grouping_transition_risk and \n transition_risk_category for `austria`", fill = "transition risk category")
plot_bar_plot_profile(avg_transition_risk_equal_weight_per_benchmark_country_risk_germany, "Average `transition_risk_profile_equal_weight`") +
  labs(x = "Average transition risk category under \n equal weight assumption for Germany", y = "Group", title = "Average transition risk category under \n equal weight assumption per \n grouping_transition_risk and \n transition_risk_category for `germany`", fill = "transition risk category")
plot_bar_plot_profile(avg_transition_risk_equal_weight_per_benchmark_country_risk_netherlands, "Average `transition_risk_profile_equal_weight`") +
  labs(x = "Average transition risk category under \n equal weight assumption for Netherlands", y = "Group", title = "Average transition risk category under \n equal weight assumption per \n grouping_transition_risk and \n transition_risk_category `netherlands`", fill = "transition risk category")
plot_bar_plot_profile(avg_transition_risk_equal_weight_per_benchmark_country_risk_spain, "Average `transition_risk_profile_equal_weight`") +
  labs(x = "Average transition risk category under \n equal weight assumption for Spain", y = "Group", title = "Average transition risk category under \n equal weight assumption per \n grouping_transition_risk and \n transition_risk_category for `spain`", fill = "transition risk category")
```

### Average `transition_risk_profile_best_case` per `grouping_transition_risk` and `transition_risk_category` for a country

```{r, warning=FALSE, echo=FALSE}
avg_transition_risk_best_case_per_benchmark_country_risk_france <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_best_case", "france") |>
  rename("Average `transition_risk_profile_best_case`" = "proportion")
avg_transition_risk_best_case_per_benchmark_country_risk_austria <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_best_case", "austria") |>
  rename("Average `transition_risk_profile_best_case`" = "proportion")
avg_transition_risk_best_case_per_benchmark_country_risk_germany <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_best_case", "germany") |>
  rename("Average `transition_risk_profile_best_case`" = "proportion")
avg_transition_risk_best_case_per_benchmark_country_risk_netherlands <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_best_case", "netherlands") |>
  rename("Average `transition_risk_profile_best_case`" = "proportion")
avg_transition_risk_best_case_per_benchmark_country_risk_spain <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_best_case", "spain") |>
  rename("Average `transition_risk_profile_best_case`" = "proportion")
```

#### Bar plots

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_transition_risk_best_case_per_benchmark_country_risk_france, "Average `transition_risk_profile_best_case`") +
  labs(x = "Average transition risk category under \n best case assumption for France", y = "Group", title = "Average transition risk category under \n best case assumption per \n grouping_transition_risk and \n transition_risk_category for `france`", fill = "transition risk category")
plot_bar_plot_profile(avg_transition_risk_best_case_per_benchmark_country_risk_austria, "Average `transition_risk_profile_best_case`") +
  labs(x = "Average transition risk category under \n best case assumption for Austria", y = "Group", title = "Average transition risk category under \n best case assumption per \n grouping_transition_risk and \n transition_risk_category for `austria`", fill = "transition risk category")
plot_bar_plot_profile(avg_transition_risk_best_case_per_benchmark_country_risk_germany, "Average `transition_risk_profile_best_case`") +
  labs(x = "Average transition risk category under \n best case assumption for Germany", y = "Group", title = "Average transition risk category under \n best case assumption per \n grouping_transition_risk and \n transition_risk_category for `germany`", fill = "transition risk category")
plot_bar_plot_profile(avg_transition_risk_best_case_per_benchmark_country_risk_netherlands, "Average `transition_risk_profile_best_case`") +
  labs(x = "Average transition risk category under \n best case assumption for Netherlands", y = "Group", title = "Average transition risk category under \n best case assumption per \n grouping_transition_risk and \n transition_risk_category for `netherlands`", fill = "transition risk category")
plot_bar_plot_profile(avg_transition_risk_best_case_per_benchmark_country_risk_spain, "Average `transition_risk_profile_best_case`") +
  labs(x = "Average transition risk category under \n best case assumption for Spain", y = "Group", title = "Average transition risk category under \n best case assumption per \n grouping_transition_risk and \n transition_risk_category for `spain`", fill = "transition risk category")
```

### Average `transition_risk_profile_worst_case` per `grouping_transition_risk` and `transition_risk_category` for a country

```{r, warning=FALSE, echo=FALSE}
avg_transition_risk_worst_case_per_benchmark_country_risk_france <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_worst_case", "france") |>
  rename("Average `transition_risk_profile_worst_case`" = "proportion")
avg_transition_risk_worst_case_per_benchmark_country_risk_austria <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_worst_case", "austria") |>
  rename("Average `transition_risk_profile_worst_case`" = "proportion")
avg_transition_risk_worst_case_per_benchmark_country_risk_germany <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_worst_case", "germany") |>
  rename("Average `transition_risk_profile_worst_case`" = "proportion")
avg_transition_risk_worst_case_per_benchmark_country_risk_netherlands <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_worst_case", "netherlands") |>
  rename("Average `transition_risk_profile_worst_case`" = "proportion")
avg_transition_risk_worst_case_per_benchmark_country_risk_spain <- avg_per_benchmark_country_risk_category(transition_risk_product_example, "transition_risk_profile_worst_case", "spain") |>
  rename("Average `transition_risk_profile_worst_case`" = "proportion")
```

#### Bar plots

```{r, echo = FALSE, warning=FALSE}
plot_bar_plot_profile(avg_transition_risk_worst_case_per_benchmark_country_risk_france, "Average `transition_risk_profile_worst_case`") +
  labs(x = "Average transition risk category under \n worst case assumption for France", y = "Group", title = "Average transition risk category under \n worst case assumption per \n  grouping_transition_risk and \n transition_risk_category for `france`", fill = "transition risk category")
plot_bar_plot_profile(avg_transition_risk_worst_case_per_benchmark_country_risk_austria, "Average `transition_risk_profile_worst_case`") +
  labs(x = "Average transition risk category under \n worst case assumption for Austria", y = "Group", title = "Average transition risk category under \n worst case assumption per \n  grouping_transition_risk and \n transition_risk_category for `austria`", fill = "transition risk category")
plot_bar_plot_profile(avg_transition_risk_worst_case_per_benchmark_country_risk_germany, "Average `transition_risk_profile_worst_case`") +
  labs(x = "Average transition risk category under \n worst case assumption for Germany", y = "Group", title = "Average transition risk category under \n worst case assumption per \n  grouping_transition_risk and \n transition_risk_category for `germany`", fill = "transition risk category")
plot_bar_plot_profile(avg_transition_risk_worst_case_per_benchmark_country_risk_netherlands, "Average `transition_risk_profile_worst_case`") +
  labs(x = "Average transition risk category under \n worst case assumption for Netherlands", y = "Group", title = "Average transition risk category under \n worst case assumption per \n  grouping_transition_risk and \n transition_risk_category for `netherlands`", fill = "transition risk category")
plot_bar_plot_profile(avg_transition_risk_worst_case_per_benchmark_country_risk_spain, "Average `transition_risk_profile_worst_case`") +
  labs(x = "Average transition risk category under \n worst case assumption for Spain", y = "Group", title = "Average transition risk category under \n worst case assumption per \n  grouping_transition_risk and \n transition_risk_category for `spain`", fill = "transition risk category")
```

### Example company-level output of transition risk profile for best case and worst case

```{r, warning=FALSE, echo=FALSE}
# read_csv("transition_risk_profile_at_company_level_all_countries_wide_22_08_24.csv")
transition_risk_company_example <- example_transition_risk_company_transition_risk_avg_best_case_worst_case()
kable(transition_risk_company_example |> head(20))
```

### Descriptive analysis of `avg_transition_risk_equal_weight` per `grouping_transition_risk`

```{r, warning=FALSE, echo=FALSE}
avg_transition_risk_per_benchmark <- function(data, col) {
  data |>
    select(all_of(c("companies_id", "grouping_transition_risk", col))) |>
    distinct() |>
    mutate(sum_mode = sum(.data[[col]], na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate(distinct_comp = n_distinct(companies_id, na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate(average = sum_mode / distinct_comp) |>
    mutate(median = median(.data[[col]], na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate("25th_quantile" = quantile(.data[[col]], 0.25, na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate("75th_quantile" = quantile(.data[[col]], 0.75, na.rm = TRUE), .by = "grouping_transition_risk") |>
    select(-all_of(c("sum_mode", col, "companies_id", "distinct_comp"))) |>
    distinct() |>
    filter(str_detect(grouping_transition_risk, "all|tilt_subsector")) |>
    filter(!str_detect(grouping_transition_risk, "NA|unit")) |>
    arrange(grouping_transition_risk)
}
avg_transition_risk_equal_weight_per_benchmark <- avg_transition_risk_per_benchmark(transition_risk_company_example, "avg_transition_risk_equal_weight")

kable(avg_transition_risk_equal_weight_per_benchmark, align = "lcccc", caption = "Descriptive analysis of `avg_transition_risk_equal_weight` per grouping_transition_risk", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(2:5, width = "3cm") |>
  add_header_above(c(" ", "avg_transition_risk_equal_weight" = 4))
```

### Descriptive analysis of `avg_transition_risk_best_case` per `grouping_transition_risk`

```{r, warning=FALSE, echo=FALSE}
avg_transition_risk_best_case_per_benchmark <- avg_transition_risk_per_benchmark(transition_risk_company_example, "avg_transition_risk_best_case")

kable(avg_transition_risk_best_case_per_benchmark, align = "lcccc", caption = "Descriptive analysis of `avg_transition_risk_best_case` per grouping_transition_risk", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(2:5, width = "3cm") |>
  add_header_above(c(" ", "avg_transition_risk_best_case" = 4))
```

### Descriptive analysis of `avg_transition_risk_worst_case` per `grouping_transition_risk`

```{r, warning=FALSE, echo=FALSE}
avg_transition_risk_worst_case_per_benchmark <- avg_transition_risk_per_benchmark(transition_risk_company_example, "avg_transition_risk_worst_case")

kable(avg_transition_risk_worst_case_per_benchmark, align = "lcccc", caption = "Descriptive analysis of `avg_transition_risk_worst_case` per grouping_transition_risk", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(2:5, width = "3cm") |>
  add_header_above(c(" ", "avg_transition_risk_worst_case" = 4))
```

### Descriptive analysis of `avg_transition_risk_equal_weight` per `grouping_transition_risk` for a country

```{r, warning=FALSE, echo=FALSE}
avg_transition_risk_per_benchmark_country <- function(data, col, country_value) {
  data |>
    select(all_of(c("country", "companies_id", "grouping_transition_risk", col))) |>
    distinct() |>
    filter(country == country_value) |>
    mutate(sum_mode = sum(.data[[col]], na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate(distinct_comp = n_distinct(companies_id, na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate(average = sum_mode / distinct_comp) |>
    mutate(median = median(.data[[col]], na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate("25th_quantile" = quantile(.data[[col]], 0.25, na.rm = TRUE), .by = "grouping_transition_risk") |>
    mutate("75th_quantile" = quantile(.data[[col]], 0.75, na.rm = TRUE), .by = "grouping_transition_risk") |>
    select(-all_of(c("sum_mode", col, "companies_id", "distinct_comp"))) |>
    distinct() |>
    filter(str_detect(grouping_transition_risk, "all|tilt_subsector")) |>
    filter(!str_detect(grouping_transition_risk, "NA|unit")) |>
    arrange(grouping_transition_risk)
}
avg_transition_risk_equal_weight_per_benchmark_france  <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_equal_weight", "france")
avg_transition_risk_equal_weight_per_benchmark_austria  <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_equal_weight", "austria")
avg_transition_risk_equal_weight_per_benchmark_germany  <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_equal_weight", "germany")
avg_transition_risk_equal_weight_per_benchmark_netherlands  <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_equal_weight", "netherlands")
avg_transition_risk_equal_weight_per_benchmark_spain  <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_equal_weight", "spain")
```

```{r, warning=FALSE, echo=FALSE}
kable(avg_transition_risk_equal_weight_per_benchmark_france, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_equal_weight` per grouping_transition_risk for country `france`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_equal_weight" = 4))
kable(avg_transition_risk_equal_weight_per_benchmark_austria, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_equal_weight` per grouping_transition_risk for country `austria`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_equal_weight" = 4))
kable(avg_transition_risk_equal_weight_per_benchmark_germany, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_equal_weight` per grouping_transition_risk for country `germany`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_equal_weight" = 4))
kable(avg_transition_risk_equal_weight_per_benchmark_netherlands, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_equal_weight` per grouping_transition_risk for country `netherlands`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_equal_weight" = 4))
kable(avg_transition_risk_equal_weight_per_benchmark_spain, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_equal_weight` per grouping_transition_risk for country `spain`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_equal_weight" = 4))
```

### Descriptive analysis of `avg_transition_risk_best_case` per `grouping_transition_risk` for a country

```{r, warning=FALSE, echo=FALSE}
avg_transition_risk_best_case_per_benchmark_france  <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_best_case", "france")
avg_transition_risk_best_case_per_benchmark_austria  <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_best_case", "austria")
avg_transition_risk_best_case_per_benchmark_germany  <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_best_case", "germany")
avg_transition_risk_best_case_per_benchmark_netherlands  <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_best_case", "netherlands")
avg_transition_risk_best_case_per_benchmark_spain  <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_best_case", "spain")
```

```{r, warning=FALSE, echo=FALSE}
kable(avg_transition_risk_best_case_per_benchmark_france, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_best_case` per grouping_transition_risk for country `france`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_best_case" = 4))
kable(avg_transition_risk_best_case_per_benchmark_austria, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_best_case` per grouping_transition_risk for country `austria`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_best_case" = 4))
kable(avg_transition_risk_best_case_per_benchmark_germany, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_best_case` per grouping_transition_risk for country `germany`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_best_case" = 4))
kable(avg_transition_risk_best_case_per_benchmark_netherlands, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_best_case` per grouping_transition_risk for country `netherlands`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_best_case" = 4))
kable(avg_transition_risk_best_case_per_benchmark_spain, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_best_case` per grouping_transition_risk for country `spain`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_best_case" = 4))
```

### Descriptive analysis of `avg_transition_risk_worst_case` per `grouping_transition_risk` for a country

```{r, warning=FALSE, echo=FALSE}
avg_transition_risk_worst_case_per_benchmark_france <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_worst_case", "france")
avg_transition_risk_worst_case_per_benchmark_austria <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_worst_case", "austria")
avg_transition_risk_worst_case_per_benchmark_germany <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_worst_case", "germany")
avg_transition_risk_worst_case_per_benchmark_netherlands <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_worst_case", "netherlands")
avg_transition_risk_worst_case_per_benchmark_spain <- avg_transition_risk_per_benchmark_country(transition_risk_company_example, "avg_transition_risk_worst_case", "spain")
```

```{r, warning=FALSE, echo=FALSE}
kable(avg_transition_risk_worst_case_per_benchmark_france, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_worst_case` per grouping_transition_risk for country `france`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_worst_case" = 4))
kable(avg_transition_risk_worst_case_per_benchmark_austria, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_worst_case` per grouping_transition_risk for country `austria`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_worst_case" = 4))
kable(avg_transition_risk_worst_case_per_benchmark_germany, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_worst_case` per grouping_transition_risk for country `germany`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_worst_case" = 4))
kable(avg_transition_risk_worst_case_per_benchmark_netherlands, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_worst_case` per grouping_transition_risk for country `netherlands`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_worst_case" = 4))
kable(avg_transition_risk_worst_case_per_benchmark_spain, align = "llcccc", caption = "Descriptive analysis of `avg_transition_risk_worst_case` per grouping_transition_risk for country `spain`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "avg_transition_risk_worst_case" = 4))
```
