---
title: "Descriptive analysis of co2_footprint per benchmark"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This article shows how to calculate the descriptive analysis of co2_footprint per
benchmark using product-level output of Emissions profile indicator.

```{r setup}
library(tiltDataAnalysis)
library(tibble)

options(readr.show_col_types = FALSE)
```

Subset of product-level output of Emissions profile.

```{r}
emission_product_example <- example_emission_product_co2_des_analysis()
emission_product_example
```

This example calculates the descriptive analysis for benchmark "all".
 
```{r}
co2_all <- calculate_co2_descriptive_analysis_per_benchmark(
   emission_product_example,
   "all"
 )
co2_all
```

This example calculates the descriptive analysis for benchmark "tilt_subsector".
 
```{r}
co2_tilt_subsector <- calculate_co2_descriptive_analysis_per_benchmark(
   emission_product_example,
   "tilt_subsector"
 )
co2_tilt_subsector
```

This example calculates the descriptive analysis for benchmark "unit_tilt_subsector".
 
```{r}
co2_unit_tilt_subsector <- calculate_co2_descriptive_analysis_per_benchmark(
   emission_product_example,
   "unit_tilt_subsector"
 )
co2_unit_tilt_subsector
```

Similarly, function `calculate_co2_descriptive_analysis_per_benchmark()` is used 
to calculate descriptive analysis of co2_footprint for benchmarks `unit`, 
`isic_4digit`, and `unit_isic_4digit`(all six emissions' 
profile benchmarks).
