---
title: "Descriptive analysis of co2_footprint per benchmark"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This article shows how to calculate the descriptive analysis of co2_footprint per
benchmark using product-level output of Emissions profile indicator.

```{r setup}
library(tiltDataAnalysis)
library(tibble)

options(readr.show_col_types = FALSE)
```

Subset of product-level output of Emissions profile.

```{r}
emission_product_example <- tribble(
           ~benchmark, ~tilt_subsector, ~co2_footprint,   ~ep_product,
     "tilt_subsector",     "chemicals",              1,       "water",
     "tilt_subsector",     "chemicals",              4,  "television",
     "tilt_subsector",     "chemicals",              9,      "tables",
     "tilt_subsector",     "chemicals",              8, "electricity",
     "tilt_subsector",     "chemicals",       NA_real_,        "meat",
     "tilt_subsector",  "iron & steel",              1,      "tables",
     "tilt_subsector",  "iron & steel",              2,       "water",
     "tilt_subsector",  "iron & steel",              4,        "tent"
   )
emission_product_example
```

This example calculates the descriptive analysis for benchmark "tilt_subsector".
 
```{r}
output <- calculate_co2_footprint_descriptive_analysis_per_benchmark(
   emission_product_example,
   "tilt_subsector"
 )
output
```

Similarly, function `calculate_co2_footprint_descriptive_analysis_per_benchmark()`
is used to create descriptive analysis of co2_footprint for benchmarks `all`, 
`unit`, `isic_4digit`, `unit_isic_4digit`, and `unit_tilt_subsector` (all six
emissions' profile benchmarks).
