---
title: "Descriptive analysis of best case and worst case for sector profile"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Roboto+Condensed:wght@400;700&display=swap');

table {
  font-family: 'Roboto Condensed', sans-serif;
}
```

This article shows how to calculate the descriptive analysis of equal weight,
best case, and worst case for sector profile.

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
library(tiltDataAnalysis)
library(kableExtra)
library(dplyr)
library(knitr)
library(ggplot2)
library(stringr)
options(readr.show_col_types = FALSE)
```

### Example company-level output of transition risk profile for best case and worst case of sector profile 

```{r, warning=FALSE, echo=FALSE}
transition_risk_company_example <- example_transition_risk_company_sector_avg_best_case_worst_case()
kable(transition_risk_company_example |> head(20))
```

### Descriptive analysis of `sector_target_avg_equal_weight` per grouping_sector

```{r, warning=FALSE, echo=FALSE}
sector_target_avg_per_benchmark <- function(data, col) {
  data |>
    select(all_of(c("companies_id", "scenario", "year", col))) |>
    distinct() |>
    mutate(grouping_sector = paste(.data$scenario, .data$year, sep = "_")) |>
    select(-c("scenario", "year")) |>
    mutate(sum_mode = sum(.data[[col]], na.rm = TRUE), .by = "grouping_sector") |>
    mutate(distinct_comp = n_distinct(companies_id, na.rm = TRUE), .by = "grouping_sector") |>
    mutate(average = sum_mode / distinct_comp) |>
    mutate(median = median(.data[[col]], na.rm = TRUE), .by = "grouping_sector") |>
    mutate("25th_quantile" = quantile(.data[[col]], 0.25, na.rm = TRUE), .by = "grouping_sector") |>
    mutate("75th_quantile" = quantile(.data[[col]], 0.75, na.rm = TRUE), .by = "grouping_sector") |>
    select(-all_of(c("sum_mode", col, "companies_id", "distinct_comp"))) |>
    distinct() |>
    filter(!str_detect(grouping_sector, "NA"))
}
sector_target_avg_equal_weight_per_benchmark <- sector_target_avg_per_benchmark(transition_risk_company_example, "sector_target_avg_equal_weight")

kable(sector_target_avg_equal_weight_per_benchmark, align = "lcccc", caption = "Descriptive analysis of `sector_target_avg_equal_weight` per grouping_sector", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(2:5, width = "3cm") |>
  add_header_above(c(" ", "sector_target_avg_equal_weight" = 4))
```

### Descriptive analysis of `sector_target_avg_best_case` per grouping_sector

```{r, warning=FALSE, echo=FALSE}
sector_target_avg_best_case_per_benchmark <- sector_target_avg_per_benchmark(transition_risk_company_example, "sector_target_avg_best_case") 

kable(sector_target_avg_best_case_per_benchmark, align = "lcccc", caption = "Descriptive analysis of `sector_target_avg_best_case` per grouping_sector", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(2:5, width = "3cm") |>
  add_header_above(c(" ", "sector_target_avg_best_case" = 4))
```

### Descriptive analysis of `sector_target_avg_worst_case` per grouping_sector

```{r, warning=FALSE, echo=FALSE}
sector_target_avg_worst_case_per_benchmark <- sector_target_avg_per_benchmark(transition_risk_company_example, "sector_target_avg_worst_case")

kable(sector_target_avg_worst_case_per_benchmark, align = "lcccc", caption = "Descriptive analysis of `sector_target_avg_worst_case` per grouping_sector", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(2:5, width = "3cm") |>
  add_header_above(c(" ", "sector_target_avg_worst_case" = 4))
```

### Descriptive analysis of `sector_target_avg_equal_weight` per grouping_sector for a country

```{r, warning=FALSE, echo=FALSE}
sector_target_avg_per_benchmark_country <- function(data, col, country_value) {
  data |>
    select(all_of(c("country", "companies_id", "scenario", "year", col))) |>
    distinct() |>
    mutate(grouping_sector = paste(.data$scenario, .data$year, sep = "_")) |>
    select(-c("scenario", "year")) |>
    filter(country == country_value) |>
    mutate(sum_mode = sum(.data[[col]], na.rm = TRUE), .by = "grouping_sector") |>
    mutate(distinct_comp = n_distinct(companies_id, na.rm = TRUE), .by = "grouping_sector") |>
    mutate(average = sum_mode / distinct_comp) |>
    mutate(median = median(.data[[col]], na.rm = TRUE), .by = "grouping_sector") |>
    mutate("25th_quantile" = quantile(.data[[col]], 0.25, na.rm = TRUE), .by = "grouping_sector") |>
    mutate("75th_quantile" = quantile(.data[[col]], 0.75, na.rm = TRUE), .by = "grouping_sector") |>
    select(-all_of(c("sum_mode", col, "companies_id", "distinct_comp"))) |>
    distinct() |>
    filter(!str_detect(grouping_sector, "NA"))
}

sector_target_avg_equal_weight_per_benchmark_france <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_equal_weight", "france")
sector_target_avg_equal_weight_per_benchmark_austria <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_equal_weight", "austria")
sector_target_avg_equal_weight_per_benchmark_germany <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_equal_weight", "germany")
sector_target_avg_equal_weight_per_benchmark_netherlands <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_equal_weight", "netherlands")
sector_target_avg_equal_weight_per_benchmark_spain <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_equal_weight", "spain")
```

```{r, warning=FALSE, echo=FALSE}
kable(sector_target_avg_equal_weight_per_benchmark_france, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_equal_weight` per grouping_sector for country `france`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_equal_weight" = 4))
kable(sector_target_avg_equal_weight_per_benchmark_austria, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_equal_weight` per grouping_sector for country `austria`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_equal_weight" = 4))
kable(sector_target_avg_equal_weight_per_benchmark_germany, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_equal_weight` per grouping_sector for country `germany`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_equal_weight" = 4))
kable(sector_target_avg_equal_weight_per_benchmark_netherlands, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_equal_weight` per grouping_sector for country `netherlands`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_equal_weight" = 4))
kable(sector_target_avg_equal_weight_per_benchmark_spain, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_equal_weight` per grouping_sector for country `spain`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_equal_weight" = 4))
```

### Descriptive analysis of `sector_target_avg_best_case` per grouping_sector for a country

```{r, warning=FALSE, echo=FALSE}
sector_target_avg_best_case_per_benchmark_france <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_best_case", "france")
sector_target_avg_best_case_per_benchmark_austria <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_best_case", "austria")
sector_target_avg_best_case_per_benchmark_germany <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_best_case", "germany")
sector_target_avg_best_case_per_benchmark_netherlands <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_best_case", "netherlands")
sector_target_avg_best_case_per_benchmark_spain <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_best_case", "spain")
```

```{r, warning=FALSE, echo=FALSE}
kable(sector_target_avg_best_case_per_benchmark_france, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_best_case` per grouping_sector for country `france`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_best_case" = 4))
kable(sector_target_avg_best_case_per_benchmark_austria, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_best_case` per grouping_sector for country `austria`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_best_case" = 4))
kable(sector_target_avg_best_case_per_benchmark_germany, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_best_case` per grouping_sector for country `germany`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_best_case" = 4))
kable(sector_target_avg_best_case_per_benchmark_netherlands, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_best_case` per grouping_sector for country `netherlands`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_best_case" = 4))
kable(sector_target_avg_best_case_per_benchmark_spain, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_best_case` per grouping_sector for country `spain`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_best_case" = 4))
```

### Descriptive analysis of `sector_target_avg_worst_case` per grouping_sector for a country

```{r, warning=FALSE, echo=FALSE}
sector_target_avg_worst_case_per_benchmark_france <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_worst_case", "france")
sector_target_avg_worst_case_per_benchmark_austria <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_worst_case", "austria")
sector_target_avg_worst_case_per_benchmark_germany <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_worst_case", "germany")
sector_target_avg_worst_case_per_benchmark_netherlands <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_worst_case", "netherlands")
sector_target_avg_worst_case_per_benchmark_spain <- sector_target_avg_per_benchmark_country(transition_risk_company_example, "sector_target_avg_worst_case", "spain")
```

```{r, warning=FALSE, echo=FALSE}
kable(sector_target_avg_worst_case_per_benchmark_france, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_worst_case` per grouping_sector for country `france`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_worst_case" = 4))
kable(sector_target_avg_worst_case_per_benchmark_austria, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_worst_case` per grouping_sector for country `austria`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_worst_case" = 4))
kable(sector_target_avg_worst_case_per_benchmark_germany, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_worst_case` per grouping_sector for country `germany`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_worst_case" = 4))
kable(sector_target_avg_worst_case_per_benchmark_netherlands, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_worst_case` per grouping_sector for country `netherlands`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_worst_case" = 4))
kable(sector_target_avg_worst_case_per_benchmark_spain, align = "llcccc", caption = "Descriptive analysis of `sector_target_avg_worst_case` per grouping_sector for country `spain`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(3:6, width = "3cm") |>
  add_header_above(c(" ", " ", "sector_target_avg_worst_case" = 4))
```
