---
title: "Descriptive analysis of co2_footprint per benchmark"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Roboto+Condensed:wght@400;700&display=swap');

table {
  font-family: 'Roboto Condensed', sans-serif;
}
```

This article shows how to calculate the descriptive analysis of co2_footprint per
benchmark using product-level output of Emissions profile indicator.

```{r setup, warning=FALSE, echo = FALSE, message=FALSE}
library(tiltDataAnalysis)
library(dplyr)
library(tibble)
library(kableExtra)
library(knitr)
library(stringr)
options(readr.show_col_types = FALSE)
```

### Example subset of product-level output of Emissions profile.

```{r, echo=FALSE}
emission_product_example <- example_emission_product_co2_des_analysis()
kable(emission_product_example |> head(20))
```

### Descriptive analysis for benchmark "all"
 
```{r, echo=FALSE}
co2_all <- calculate_co2_descriptive_analysis_per_benchmark(
   emission_product_example,
   "all"
 )
kable(co2_all, align = "ccccc", caption = "Descriptive analysis for benchmark `all`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(1, width = "4cm") |>
  column_spec(2:5, width = "2.5cm") 
```

### Descriptive analysis for benchmark "tilt_subsector"
 
```{r, echo=FALSE}
co2_tilt_subsector <- calculate_co2_descriptive_analysis_per_benchmark(
   emission_product_example,
   "tilt_subsector"
 ) |>
    filter(!str_detect(tilt_subsector, "NA"))

kable(co2_tilt_subsector, align = "llccccc", caption = "Descriptive analysis for benchmark `tilt_subsector`", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(2, width = "3cm") |>
  column_spec(3, width = "4cm") |>
  column_spec(4:7, width = "2.5cm") |>
  collapse_rows(columns = 1, valign = "top")
```

### Five products with lowest CO2e values

```{r, echo=FALSE}
lowest_co2 <- emission_product_example |>
  select(all_of(c("ep_product", "co2_footprint"))) |>
  distinct() |>
  arrange(.data$co2_footprint) |>
  head(5)

kable(lowest_co2, align = "lc", caption = "Five products with lowest CO2e values", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(2, width = "3cm")
```

### Five products with highest CO2e values

```{r, echo=FALSE}
highest_co2 <- emission_product_example |>
  select(all_of(c("ep_product", "co2_footprint"))) |>
  distinct() |>
  arrange(desc(.data$co2_footprint)) |>
  head(5)

kable(highest_co2, align = "lc", caption = "Five products with highest CO2e values", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(2, width = "3cm")
```
