---
title: "Descriptive analysis on amount of companies"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This article shows how to calculate the descriptive analysis on amount of 
companies for emission and sector profile.

```{r setup, warning=FALSE, echo = FALSE, message=FALSE}
library(tiltDataAnalysis)
library(dplyr)
library(knitr)
library(tidyselect)
library(kableExtra)
library(stringr)
options(readr.show_col_types = FALSE)
```

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Roboto+Condensed:wght@400;700&display=swap');

table {
  font-family: 'Roboto Condensed', sans-serif;
}
```

### Example subset of product-level output of transition risk profile.

```{r, echo=FALSE}
# read_csv("transition_risk_profile_at_product_level_all_countries_wide_22_08_24.csv")
transition_risk_product_example <- product_transition_risk |>
  select(all_of(c("companies_id", "country", "transition_risk_category", "emission_category",
                  "sector_category", "tilt_sector", "tilt_subsector", "main_activity"))) |>
  distinct() |>
  mutate(companies_id = ifelse(companies_id == "insecticidal_clownanemonefish",
                               "heliophobic_clownanemonefish", companies_id)) |>
  filter(companies_id %in% c("antimonarchy_canine", "nonphilosophical_llama",
                             "subdermal_chipmunk", "fascist_maiasaura",
                             "ironhearted_tarpan", "heliophobic_clownanemonefish",
                             "subzero_whiteeye"))
```

```{r, echo=FALSE}
kable(transition_risk_product_example |> head(10))
```

### Number of distinct companies

```{r, results='asis'}
cat("Number of distinct firms: ", n_distinct(transition_risk_product_example$companies_id))
```

### Number of companies that have atleast one product with `emission_profile`, with `sector_profile`, and with `transition_risk_category`

```{r, echo=FALSE}
companies_atleast_one_product_with_profile <- function(data, profile) {
  result <- data |>
    select(all_of(c("companies_id", profile))) |>
    filter(!is.na(.data[[profile]])) |>
    distinct()
  
  n_distinct(result$companies_id)
}
```

```{r, results='asis'}
cat("Number of firms that have atleast one product with `emission_profile`:", companies_atleast_one_product_with_profile(transition_risk_product_example, "emission_category"))
cat("Number of firms that have atleast one product with `sector_profile`:", companies_atleast_one_product_with_profile(transition_risk_product_example, "sector_category"))
cat("Number of firms that have atleast one product with `transition_risk_category`:", companies_atleast_one_product_with_profile(transition_risk_product_example, "transition_risk_category"))
```

### Number of companies that have more than one tilt_sectors

```{r, echo=FALSE}
companies_with_multiple_tilt_sectors <- function(data) {
  result <- data |>
    select(all_of(c("companies_id", "tilt_sector"))) |>
    distinct() |>
    mutate(total_tilt_sectors = n_distinct(tilt_sector, na.rm = TRUE), .by = "companies_id") |>
    filter(total_tilt_sectors > 1)
  
  n_distinct(result$companies_id)
}
```

```{r, results='asis'}
cat("Number of firms that have more than one tilt_sectors: ", companies_with_multiple_tilt_sectors(transition_risk_product_example))
```

### Number of companies that have more than one tilt_subsectors

```{r, echo=FALSE}
companies_with_multiple_tilt_subsectors <- function(data) {
  result <- data |>
    select(all_of(c("companies_id", "tilt_subsector"))) |>
    distinct() |>
    mutate(total_tilt_subsectors = n_distinct(tilt_subsector, na.rm = TRUE), .by = "companies_id") |>
    filter(total_tilt_subsectors > 1)
  
  n_distinct(result$companies_id)
}
```

```{r, results='asis'}
cat("Number of firms that have more than one tilt_subsectors: ", companies_with_multiple_tilt_subsectors(transition_risk_product_example))
```

### Number of companies per tilt_sector

```{r, echo=FALSE}
companies_per_single_benchmark <- function(data, benchmark) {
  data |>
    select(all_of(c("companies_id", benchmark))) |>
    distinct() |>
    mutate("# of firms" = n_distinct(companies_id, na.rm = TRUE), .by = benchmark) |>
    select(-all_of(c("companies_id"))) |>
    distinct() |>
    filter(!str_detect(.data[[benchmark]], "NA")) |>
    arrange(.data[[benchmark]])
}
```

```{r, warning=FALSE, echo=FALSE}
# To create CSV files. Location: https://drive.google.com/drive/folders/1PSLn5nBtO-WK3-11_u857Q0yRtdoC6J9
# result <- companies_per_single_benchmark(transition_risk_product_example, "tilt_sector")
# readr::write_csv(result, file = "number_of_firms_per_tilt_sector.csv")
```

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_single_benchmark(transition_risk_product_example, "tilt_sector"), align = "lc", caption = "# of firms per tilt_sector", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(1:2, width = "3cm")
```

### Number of companies per tilt_subsector

```{r, warning=FALSE, echo=FALSE}
# result <- companies_per_single_benchmark(transition_risk_product_example, "tilt_subsector")
# readr::write_csv(result, file = "number_of_firms_per_tilt_subsector.csv")
```

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_single_benchmark(transition_risk_product_example, "tilt_subsector"), align = "lc", caption = "# of firms per tilt_subsector", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(1:2, width = "3cm")
```

### Number of companies per country

```{r, warning=FALSE, echo=FALSE}
# result <- companies_per_single_benchmark(transition_risk_product_example, "country")
# readr::write_csv(result, file = "number_of_firms_per_country.csv")
```

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_single_benchmark(transition_risk_product_example, "country"), align = "lc", caption = "# of firms per country", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(1:2, width = "3cm")
```

### Number of companies per country and tilt_sector

```{r, echo=FALSE}
companies_per_double_benchmark <- function(data, benchmark_first, benchmark_second) {
  data |>
    select(all_of(c("companies_id", benchmark_first, benchmark_second))) |>
    distinct() |>
    mutate("# of firms" = n_distinct(companies_id, na.rm = TRUE), .by = c(benchmark_first, benchmark_second)) |>
    select(-all_of(c("companies_id"))) |>
    distinct() |>
    filter(!str_detect(.data[[benchmark_first]], "NA")) |>
    filter(!str_detect(.data[[benchmark_second]], "NA")) |>
    arrange(.data[[benchmark_first]], .data[[benchmark_second]])
}
```

```{r, warning=FALSE, echo=FALSE}
# result <- companies_per_double_benchmark(transition_risk_product_example, "country", "tilt_sector")
# readr::write_csv(result, file = "number_of_firms_per_country_and_tilt_sector.csv")
```

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_double_benchmark(transition_risk_product_example, "country", "tilt_sector"), align = "llc", caption = "# of firms per country and tilt_sector", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(1:3, width = "3cm") |>
  collapse_rows(columns = 1, valign = "top")
```

### Number of companies per country and tilt_subsector

```{r, warning=FALSE, echo=FALSE}
# result <- companies_per_double_benchmark(transition_risk_product_example, "country", "tilt_subsector")
# readr::write_csv(result, file = "number_of_firms_per_country_and_tilt_subsector.csv")
```

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_double_benchmark(transition_risk_product_example, "country", "tilt_subsector"), align = "llc", caption = "# of firms per country and tilt_subsector", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(1:3, width = "3cm") |>
  collapse_rows(columns = 1, valign = "top")
```

### Number of companies per main_activity

```{r, warning=FALSE, echo=FALSE}
# result <- companies_per_single_benchmark(transition_risk_product_example, "main_activity")
# readr::write_csv(result, file = "number_of_firms_per_main_activity.csv")
```

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_single_benchmark(transition_risk_product_example, "main_activity"), align = "lc", caption = "# of firms per main_activity", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(1:2, width = "3cm") 
```

### Number of companies per main_activity and tilt_sector

```{r, warning=FALSE, echo=FALSE}
# result <- companies_per_double_benchmark(transition_risk_product_example, "main_activity", "tilt_sector")
# readr::write_csv(result, file = "number_of_firms_per_main_activity_and_tilt_sector.csv")
```

```{r, warning=FALSE, echo=FALSE}
result <- companies_per_double_benchmark(transition_risk_product_example, "main_activity", "tilt_sector") |>
  filter(tilt_sector %in% c("construction", "industry", "land use"))
kable(result, align = "llc", caption = "# of firms per main_activity and tilt_sector", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(1:3, width = "3cm") |>
  collapse_rows(columns = 1, valign = "top")
```

### Number of companies per main_activity and tilt_subsector

```{r, warning=FALSE, echo=FALSE}
# result <- companies_per_double_benchmark(transition_risk_product_example, "main_activity", "tilt_subsector")
# readr::write_csv(result, file = "number_of_firms_per_main_activity_and_tilt_subsector.csv")
```

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_double_benchmark(transition_risk_product_example, "main_activity", "tilt_subsector"), align = "llc", caption = "# of firms per main_activity and tilt_subsector", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(1:3, width = "3cm") |>
  collapse_rows(columns = 1, valign = "top")
```

### Number of companies per main_activity and country

```{r, warning=FALSE, echo=FALSE}
# result <- companies_per_double_benchmark(transition_risk_product_example, "main_activity", "country")
# readr::write_csv(result, file = "number_of_firms_per_main_activity_and_country.csv")
```

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_double_benchmark(transition_risk_product_example, "main_activity", "country"), align = "llc", caption = "# of firms per main_activity and country", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(1:3, width = "3cm") |>
  collapse_rows(columns = 1, valign = "top")
```

### Number of companies per main_activity, country, and tilt_sector

```{r, echo=FALSE}
companies_per_main_activity_country_tilt_sector <- function(data) {
  data |>
    select(all_of(c("companies_id", "main_activity", "country", "tilt_sector"))) |>
    distinct() |>
    mutate("# of firms" = n_distinct(companies_id, na.rm = TRUE), .by = c("main_activity", "country", "tilt_sector")) |>
    select(-all_of(c("companies_id"))) |>
    distinct() |>
    filter(!str_detect(tilt_sector, "NA")) |>
    arrange(main_activity, country, tilt_sector)
}
```

```{r, warning=FALSE, echo=FALSE}
# result <- companies_per_main_activity_country_tilt_sector(transition_risk_product_example)
# readr::write_csv(result, file = "number_of_firms_per_main_activity_country_tilt_sector.csv")
```

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_main_activity_country_tilt_sector(transition_risk_product_example), align = "lllc",  caption = "# of firms per main_activity, country, and tilt_sector", escape = F) |>
  kable_classic(full_width = F, html_font = "Roboto Condensed") |>
  column_spec(1:4, width = "3cm") |>
  collapse_rows(columns = 1:2, valign = "top")
```
