---
title: "Descriptive analysis of co2_footprint per benchmark"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This article shows how to calculate the descriptive analysis of co2_footprint per
benchmark using product-level output of Emissions profile indicator.

```{r setup, warning=FALSE, echo = FALSE, message=FALSE}
library(tiltDataAnalysis)
library(tibble)
library(kableExtra)
library(knitr)
options(readr.show_col_types = FALSE)
```

### Example subset of product-level output of Emissions profile.

```{r}
emission_product_example <- example_emission_product_co2_des_analysis()
kable(emission_product_example)
```

### Descriptive analysis for benchmark "all"
 
```{r}
co2_all <- calculate_co2_descriptive_analysis_per_benchmark(
   emission_product_example,
   "all"
 )
kable(co2_all, align = "ccccccc", caption = "Descriptive analysis for benchmark `all`", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:7, width = "2.5cm") 
```

### Descriptive analysis for benchmark "unit"
 
```{r}
co2_unit <- calculate_co2_descriptive_analysis_per_benchmark(
   emission_product_example,
   "unit"
 )

kable(co2_unit, align = "lccccccc", caption = "Descriptive analysis for benchmark `unit`", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:8, width = "2.5cm")
```

### Descriptive analysis for benchmark "isic_4digit"
 
```{r}
co2_isic_4digit <- calculate_co2_descriptive_analysis_per_benchmark(
   emission_product_example,
   "isic_4digit"
 )

kable(co2_isic_4digit, align = "lccccccc", caption = "Descriptive analysis for benchmark `isic_4digit`", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:8, width = "2.5cm")
```

### Descriptive analysis for benchmark "tilt_subsector"
 
```{r}
co2_tilt_subsector <- calculate_co2_descriptive_analysis_per_benchmark(
   emission_product_example,
   "tilt_subsector"
 )

kable(co2_tilt_subsector, align = "lccccccc", caption = "Descriptive analysis for benchmark `tilt_subsector`", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:8, width = "2.5cm")
```

### Descriptive analysis for benchmark "unit_tilt_subsector"
 
```{r}
co2_unit_tilt_subsector <- calculate_co2_descriptive_analysis_per_benchmark(
   emission_product_example,
   "unit_tilt_subsector"
 )

kable(co2_unit_tilt_subsector, align = "llccccccc", caption = "Descriptive analysis for benchmark `unit_tilt_subsector`", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:9, width = "2.5cm")
```

### Descriptive analysis for benchmark "unit_isic_4digit"
 
```{r}
co2_unit_isic_4digit <- calculate_co2_descriptive_analysis_per_benchmark(
   emission_product_example,
   "unit_isic_4digit"
 )

kable(co2_unit_isic_4digit, align = "llccccccc", caption = "Descriptive analysis for benchmark `unit_isic_4digit`", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:9, width = "2.5cm")
```
