---
title: "Descriptive analysis of transition risk scores for all tilt_subsectors per scenario-year benchmark"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This article shows how to calculate the descriptive analysis of transition risk 
scores for all `tilt_subsectors` per scenario-year benchmark using product-level 
output of Transition risk profile indicator.

```{r setup}
library(tiltDataAnalysis)
options(readr.show_col_types = FALSE)
options(width = 5000)
```

Example subset of product-level output of Transition risk profile.

```{r}
transition_risk_product_example <- product_transition_risk |>
  dplyr::select(c("tilt_subsector", "scenario", "year", "transition_risk_score")) |>
  dplyr::distinct()
transition_risk_product_example |> 
  print(n = Inf)
```

Descriptive analysis for benchmark "1.5C RPS_2030".

```{r}
ipr_2030 <- calculate_trs_descriptive_analysis_per_scenario_year(
   transition_risk_product_example,
   "1.5C RPS_2030"
 )
ipr_2030
```

Descriptive analysis for benchmark "1.5C RPS_2050".

```{r}
ipr_2050 <- calculate_trs_descriptive_analysis_per_scenario_year(
   transition_risk_product_example,
   "1.5C RPS_2050"
 )
ipr_2050
```

Descriptive analysis for benchmark "NZ 2050_2030".

```{r}
weo_2030 <- calculate_trs_descriptive_analysis_per_scenario_year(
   transition_risk_product_example,
   "NZ 2050_2030"
 )
weo_2030
```

Descriptive analysis for benchmark "NZ 2050_2050".

```{r}
weo_2050 <- calculate_trs_descriptive_analysis_per_scenario_year(
   transition_risk_product_example,
   "NZ 2050_2050"
 )
weo_2050
```
