---
title: "Descriptive analysis on amount of companies"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This article shows how to calculate the descriptive analysis on amount of 
companies for emission and sector profile.

```{r setup, warning=FALSE, echo = FALSE, message=FALSE}
devtools::load_all(".")
# library(tiltDataAnalysis)
library(dplyr)
library(knitr)
library(tidyselect)
library(kableExtra)
options(readr.show_col_types = FALSE)
```

### Example subset of product-level output of emissions profile.

```{r, echo=FALSE}
emission_product_example <- product_emission |>
  select(all_of(c("companies_id", "country", "emission_profile", "tilt_sector", 
                  "tilt_subsector", "main_activity"))) |>
  distinct() |>
  mutate(companies_id = ifelse(companies_id == "insecticidal_clownanemonefish", 
                               "heliophobic_clownanemonefish", companies_id)) |>
  filter(companies_id %in% c("antimonarchy_canine", "nonphilosophical_llama", 
                             "subdermal_chipmunk", "fascist_maiasaura",
                             "ironhearted_tarpan", "heliophobic_clownanemonefish",
                             "subzero_whiteeye"))
```

```{r}
kable(emission_product_example |> head(20))
```

### Example subset of product-level output of sector profile.

```{r, echo=FALSE}
sector_product_example <- product_sector |>
  select(all_of(c("companies_id", "country", "sector_profile", "tilt_sector", 
                  "tilt_subsector", "main_activity"))) |>
  distinct() |>
  mutate(companies_id = ifelse(companies_id == "insecticidal_clownanemonefish", 
                               "heliophobic_clownanemonefish", companies_id)) |>
  filter(companies_id %in% c("antimonarchy_canine", "nonphilosophical_llama", 
                             "subdermal_chipmunk", "fascist_maiasaura",
                             "ironhearted_tarpan", "heliophobic_clownanemonefish",
                             "subzero_whiteeye"))
```

```{r}
kable(sector_product_example |> head(20))
```

### Example subset of product-level output of transition risk profile.

```{r, echo=FALSE}
transition_risk_product_example <- product_transition_risk |>
  select(all_of(c("companies_id", "country", "transition_risk_category", "tilt_sector", 
                  "tilt_subsector", "main_activity"))) |>
  distinct() |>
  mutate(companies_id = ifelse(companies_id == "insecticidal_clownanemonefish", 
                               "heliophobic_clownanemonefish", companies_id)) |>
  filter(companies_id %in% c("antimonarchy_canine", "nonphilosophical_llama", 
                             "subdermal_chipmunk", "fascist_maiasaura",
                             "ironhearted_tarpan", "heliophobic_clownanemonefish",
                             "subzero_whiteeye"))
```

```{r}
kable(transition_risk_product_example |> head(20))
```

### Number of companies for emission, sector, and transition risk profile

```{r, results='asis'}
cat("Number of companies for emission profile:", n_distinct(emission_product_example$companies_id))
cat("Number of companies for sector profile:", n_distinct(sector_product_example$companies_id))
cat("Number of companies for transition risk profile:", n_distinct(transition_risk_product_example$companies_id))
```

### Number of companies that have atleast one product with `emission_profile`, with `sector_profile`, and with `transition_risk_category`

```{r, echo=FALSE}
companies_atleast_one_product_with_profile <- function(data, profile) {
  result <- data |>
    select(all_of(c("companies_id", profile))) |>
    distinct() |>
    filter(!is.na(.data[[profile]]))
  
  n_distinct(result$companies_id)
}
```

```{r, results='asis'}
cat("Number of companies that have atleast one product with `emission_profile`:", companies_atleast_one_product_with_profile(emission_product_example, "emission_profile"))
cat("Number of companies that have atleast one product with `sector_profile`:", companies_atleast_one_product_with_profile(sector_product_example, "sector_profile"))
cat("Number of companies that have atleast one product with `transition_risk_category`:", companies_atleast_one_product_with_profile(transition_risk_product_example, "transition_risk_category"))
```

### Number of companies that have more than one tilt_sectors for emission, sector, and transition risk profile

```{r, echo=FALSE}
companies_with_multiple_tilt_sectors <- function(data) {
  result <- data |>
    select(all_of(c("companies_id", "tilt_sector"))) |>
    distinct() |>
    mutate(total_tilt_sectors = n_distinct(tilt_sector, na.rm = TRUE), .by = "companies_id") |>
    filter(total_tilt_sectors > 1)
  
  n_distinct(result$companies_id)
}
```

```{r, results='asis'}
cat("Number of companies that have more than one tilt_sectors for emission profile:", companies_with_multiple_tilt_sectors(emission_product_example))
cat("Number of companies that have more than one tilt_sectors for sector profile:", companies_with_multiple_tilt_sectors(sector_product_example))
cat("Number of companies that have more than one tilt_sectors for transition risk profile:", companies_with_multiple_tilt_sectors(transition_risk_product_example))
```

### Number of companies that have more than one tilt_subsectors for emission, sector, and transition risk profile

```{r, echo=FALSE}
companies_with_multiple_tilt_subsectors <- function(data) {
  result <- data |>
    select(all_of(c("companies_id", "tilt_subsector"))) |>
    distinct() |>
    mutate(total_tilt_subsectors = n_distinct(tilt_subsector, na.rm = TRUE), .by = "companies_id") |>
    filter(total_tilt_subsectors > 1)
  
  n_distinct(result$companies_id)
}
```

```{r, results='asis'}
cat("Number of companies that have more than one tilt_subsectors for emission profile:", companies_with_multiple_tilt_subsectors(emission_product_example))
cat("Number of companies that have more than one tilt_subsectors for sector profile:", companies_with_multiple_tilt_subsectors(sector_product_example))
cat("Number of companies that have more than one tilt_subsectors for transition risk profile:", companies_with_multiple_tilt_subsectors(transition_risk_product_example))
```

### Number of companies per tilt_sector for emission, sector, and transition risk profile

```{r, echo=FALSE}
companies_per_single_benchmark <- function(data, benchmark) {
  data |>
    select(all_of(c("companies_id", benchmark))) |>
    distinct() |>
    mutate(companies_count = n_distinct(companies_id, na.rm = TRUE), .by = benchmark) |>
    select(-all_of(c("companies_id"))) |>
    distinct() |>
    arrange(.data[[benchmark]])
}
```

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_single_benchmark(emission_product_example, "tilt_sector"), align = "lc", caption = "Number of companies per tilt_sector for emission profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:2, width = "3cm") 
kable(companies_per_single_benchmark(sector_product_example, "tilt_sector"), align = "lc", caption = "Number of companies per tilt_sector for sector profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:2, width = "3cm")
kable(companies_per_single_benchmark(transition_risk_product_example, "tilt_sector"), align = "lc", caption = "Number of companies per tilt_sector for transition risk profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:2, width = "3cm")
```

### Number of companies per tilt_subsector for emission, sector, and transition risk profile

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_single_benchmark(emission_product_example, "tilt_subsector"), align = "lc", caption = "Number of companies per tilt_subsector for emission profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:2, width = "3cm") 
kable(companies_per_single_benchmark(sector_product_example, "tilt_subsector"), align = "lc", caption = "Number of companies per tilt_subsector for sector profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:2, width = "3cm")
kable(companies_per_single_benchmark(transition_risk_product_example, "tilt_subsector"), align = "lc", caption = "Number of companies per tilt_subsector for transition risk profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:2, width = "3cm")
```

### Number of companies per country for emission, sector, and transition risk profile

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_single_benchmark(emission_product_example, "country"), align = "lc", caption = "Number of companies per country for emission profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:2, width = "3cm") 
kable(companies_per_single_benchmark(sector_product_example, "country"), align = "lc", caption = "Number of companies per country for sector profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:2, width = "3cm")
kable(companies_per_single_benchmark(transition_risk_product_example, "country"), align = "lc", caption = "Number of companies per country for transition risk profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:2, width = "3cm")
```

### Number of companies per country and tilt_sector emission, sector, and transition risk profile

```{r, echo=FALSE}
companies_per_double_benchmark <- function(data, benchmark_first, benchmark_second) {
  data |>
    select(all_of(c("companies_id", benchmark_first, benchmark_second))) |>
    distinct() |>
    mutate(companies_count = n_distinct(companies_id, na.rm = TRUE), .by = c(benchmark_first, benchmark_second)) |>
    select(-all_of(c("companies_id"))) |>
    distinct() |>
    arrange(.data[[benchmark_first]], .data[[benchmark_second]])
}
```

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_double_benchmark(emission_product_example, "country", "tilt_sector"), align = "lcc", caption = "Number of companies per country and tilt_sector for emission profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
kable(companies_per_double_benchmark(sector_product_example, "country", "tilt_sector"), align = "lcc", caption = "Number of companies per country and tilt_sector for sector profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
kable(companies_per_double_benchmark(transition_risk_product_example, "country", "tilt_sector"), align = "lcc", caption = "Number of companies per country and tilt_sector for transition risk profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
```

### Number of companies per country and tilt_subsector emission, sector, and transition risk profile

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_double_benchmark(emission_product_example, "country", "tilt_subsector"), align = "lcc", caption = "Number of companies per country and tilt_subsector for emission profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
kable(companies_per_double_benchmark(sector_product_example, "country", "tilt_subsector"), align = "lcc", caption = "Number of companies per country and tilt_subsector for sector profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
kable(companies_per_double_benchmark(transition_risk_product_example, "country", "tilt_subsector"), align = "lcc", caption = "Number of companies per country and tilt_subsector for transition risk profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
```

### Number of companies per main_activity for emission, sector, and transition risk profile

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_single_benchmark(emission_product_example, "main_activity"), align = "lc", caption = "Number of companies per main_activity for emission profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:2, width = "3cm") 
kable(companies_per_single_benchmark(sector_product_example, "main_activity"), align = "lc", caption = "Number of companies per main_activity for sector profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:2, width = "3cm") 
kable(companies_per_single_benchmark(transition_risk_product_example, "main_activity"), align = "lc", caption = "Number of companies per main_activity for transition risk profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:2, width = "3cm") 
```

### Number of companies per main_activity and tilt_sector for emission, sector, and transition risk profile

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_double_benchmark(emission_product_example, "main_activity", "tilt_sector"), align = "lcc", caption = "Number of companies per main_activity and tilt_sector for emission profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
kable(companies_per_double_benchmark(sector_product_example, "main_activity", "tilt_sector"), align = "lcc", caption = "Number of companies per main_activity and tilt_sector for sector profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
kable(companies_per_double_benchmark(transition_risk_product_example, "main_activity", "tilt_sector"), align = "lcc", caption = "Number of companies per main_activity and tilt_sector for transition risk profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
```

### Number of companies per main_activity and tilt_subsector for emission, sector, and transition risk profile

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_double_benchmark(emission_product_example, "main_activity", "tilt_subsector"), align = "lcc", caption = "Number of companies per main_activity and tilt_subsector for emission profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
kable(companies_per_double_benchmark(sector_product_example, "main_activity", "tilt_subsector"), align = "lcc", caption = "Number of companies per main_activity and tilt_subsector for sector profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
kable(companies_per_double_benchmark(transition_risk_product_example, "main_activity", "tilt_subsector"), align = "lcc", caption = "Number of companies per main_activity and tilt_subsector for transition risk profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
```

### Number of companies per main_activity and country for emission, sector, and transition risk profile

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_double_benchmark(emission_product_example, "main_activity", "country"), align = "lcc", caption = "Number of companies per main_activity and country for emission profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
kable(companies_per_double_benchmark(sector_product_example, "main_activity", "country"), align = "lcc", caption = "Number of companies per main_activity and country for sector profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
kable(companies_per_double_benchmark(transition_risk_product_example, "main_activity", "country"), align = "lcc", caption = "Number of companies per main_activity and country for transition risk profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:3, width = "3cm") 
```

### Number of companies per main_activity, country, and tilt_sector for emission, sector, and transition risk profile

```{r, echo=FALSE}
companies_per_main_activity_country_tilt_sector <- function(data) {
  data |>
    select(all_of(c("companies_id", "main_activity", "country", "tilt_sector"))) |>
    distinct() |>
    mutate(companies_count = n_distinct(companies_id, na.rm = TRUE), .by = c("main_activity", "country", "tilt_sector")) |>
    select(-all_of(c("companies_id"))) |>
    distinct() |>
    arrange(main_activity, country, tilt_sector)
}
```

```{r, warning=FALSE, echo=FALSE}
kable(companies_per_main_activity_country_tilt_sector(emission_product_example), align = "lccc", caption = "Number of companies per main_activity, country, and tilt_sector for emission profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:4, width = "3cm") 
kable(companies_per_main_activity_country_tilt_sector(sector_product_example), align = "lccc", caption = "Number of companies per main_activity, country, and tilt_sector for sector profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:4, width = "3cm") 
kable(companies_per_main_activity_country_tilt_sector(transition_risk_product_example), align = "lccc",  caption = "Number of companies per main_activity, country, and tilt_sector for transition risk profile", escape = F) |>
  kable_classic(full_width = F, html_font = "Cambria") |>
  column_spec(1:4, width = "3cm") 
```
